### 2020-06-06 doc/ms/GEBv1/WoS DB publication/WoS DB cleaning/Reference list WoS.Rmd
single project

---
title: "References WoS"
author: "Eduardo Fernández Pascual"
date: "17/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse); library(kableExtra)
load("C:/EFP/Trabayu/GitHub/sylvanseeds/data/WoSDB.RData")
References %>% select(Reference) %>% arrange(Reference) %>% kable(caption = "Appendix 1 – Data sources. List of references used to build the germination database.", booktabs = TRUE) %>% kable_styling(latex_options = c("striped", "hold_position"))
```

Refs

### 2020-06-06 doc/rev1/rev1.Rmd
single project

---
title: "Sylvan Seeds, a database and web app to explore the seed germination ecology of temperate broadleaf and mixed forests of the northern hemisphere"
subtitle: "Running title: Sylvan Seeds, a forest germination database"
output: 
  bookdown::word_document2:
    reference_docx: gebtemplate.docx
bibliography: refs.bib
csl: global-ecology-and-biogeography.csl
link-citations: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",")
})
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse); library(here); library(flextable)
load(here("results", "msnumbers.RData"))
load(here("results", "msfigs.RData"))
```

# Abstract

*Motivation* Seed traits have functional significance in all levels of plant ecology, from population dynamics to community assembly and species distribution models. Recent discussions on the utility of seed traits in ecology have highlighted the unavailability of reliable germination databases of wide geographical scope. This data paper presents a first global dataset of raw germination data, encompassing an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere. Data were gathered using a systematic literature search approach.

*Main types of variable contained* Proportion of seeds germinated in laboratory experiments, under different experimental combinations of scarification, stratification, light or darkness, and constant or alternating germination temperatures.

*Spatial location and grain* Seed lots collected throughout the biome and in neighbouring areas, with approximate geographical coordinates of the collecting sites.

*Time period and grain* Seed lots collected between 1920 and 2017.

*Major taxa and level of measurement* 326 plant species with high frequency in vegetation relevés of the biome, representing 74 families of seed plants (gymnosperms and angiosperms).

*Software format* The database is provided as a single *.csv* file. The shiny web app *Sylvan Seeds* is also presented, to explore the database and make it accessible to the wider public.

# Keywords

Temperate deciduous forests, temperate evergreen forests, temperate coniferous forests, seed traits, germination database, seed dormancy, germination temperature, alternating temperatures, light germination, dark germination

# Introduction

Seed traits have functional significance in all levels of plant ecology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942]. Recent discussions [@RN2352; @RN4655] highlighted the unavailability of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum. Seed germination is the first major developmental transition in the life of a plant, and as such it has profound effects on the plant's ecology [@RN2384]. As such, the timing of this transition is controlled by a combination of environmental signals. Amongst these are temperature [@RN2249], diurnal temperature alternation [@RN2217], light [@RN4656] and seed dormancy inductors and relievers [@RN3063]. All of these signals interact to produce a coarse- and fine-scale regulation of germination timing, integrating inputs from both seasonal climatic cycles [@RN3132] and local environmental gradients [@RN2865]. The practical consequence of this is that the response of seeds to, for example, light will depend on other conditions set by the experimenter. This makes it difficult to summarise germination “traits” into a single value in a way comparable to seed mass, specific leaf area or plant height [@RN2923], and may explain the lack of global germination databases. Germination compilations with a biogeographical background, of which the prime example today is the cornerstone book of Baskin and Baskin [-@RN3214], only provide summary information, for instance the interpreted optimal germination temperature instead of the proportion of seeds germinated across a temperature gradient.

To fill this gap, this data paper presents a first global dataset of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*). The building of the dataset was part of a research project conducted within the *sPlot* initiative [@RN4658], specifically *sPlot*’s project #12 (https://www.idiv.de/en/sdiv/working_groups/wg_pool/splot/projects.html). The goal of *sPlot* #12 was to study taxonomical and functional plant diversity in deciduous forests, which are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers. In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe [@RN4684]. At the same time, a relatively high number of classic seed biology research groups have worked within the *TBMFNH* areas, e.g. in the USA [@RN1045], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188]. For this reason, *sPlot* project #12 was chosen to incorporate a biome-wide analysis of seed traits, as it was expected that the *TBMFNH* would provide a wide scope of available data. To gather data for the project, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the *TBMFNH*. This data paper makes the database accessible to the research community. Additionally, the *Sylvan Seeds* shiny web app is presented to facilitate the exploration of the data.

# Methods

## Species list

A list of species for which to search germination data was created using vegetation relevés (i.e. records of plant species co-occurring in sampling plots) from *sPlot* [@RN4658]. The terrestrial regionalization of the *World Wildlife Fund* [@RN4667] was used to select plots according to their coordinates. To ensure that plots were a representative sample of *TBMFNH* biodiversity, they were chosen from `r MSecoregions` ecoregions distributed throughout the northern hemisphere: 17 ecoregions of the Temperate Broadleaf and Mixed Forests biome (*Appalachian mixed mesophytic forests*, *Atlantic mixed forests*, *Cantabrian mixed forests*, *Caspian Hyrcanian mixed forests*, *Central Korean deciduous forests*, *Dinaric Mountains mixed forests*, *Euxine-Colchic broadleaf forests*, *Hokkaido deciduous forests*, *Manchurian mixed forests*, *Nihonkai evergreen forests*, *Nihonkai montane deciduous forests*, *Pindus Mountains mixed forests*, *Southeastern mixed forests*, *Taiheiyo evergreen forests*, *Taiheiyo montane deciduous forests*, *Western European broadleaf forests*, *Western Great Lakes forests*), plus three neighbouring ecoregions of the Temperate Coniferous Forest biome (*Cascade Mountains leeward forests*, *Central and Southern Cascades forests*, *Eastern Cascades forests*). Although temperate broadleaf and mixed forests also occur in a smaller area of the southern hemisphere, these southern forests form a separate evolutionary and biogeographical unit, not being related by a common history like the northern hemisphere ones [@RN4684].  For this reason, they were not considered. All chosen relevés had been classified as forest plots by *sPlot*, i.e. their plant cover was dominated by tree species. The taxa names were standardized to species level with *The Plant List* [-@RN2321] using the *Taxonstand* package [@RN4660] in *R* version 3.6.2 [@RN2315]. The final vegetation database contained `r MSplots` relevés and `r MStotalspp` standardized species names, considering only seed plants (gymnosperms and angiosperms), and encompassing all forest layers. To obtain the final list of species, only species that were present in at least 5% of the relevés of an ecoregion were kept, rendering a list of `r MSfrequentspp` frequent species. There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of *TBMFNH*, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.). The result is a list of plant species that occur with relatively high frequency in forest plots of the *TBMFNH*; this includes trees, shrubs and shade-tolerant forbs and grasses, as well as common semi-open species from forest margins, secondary forests, ruderalized forest plots, etc.

## Web of Science literature search

The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)” (**Supplementary material 1**). This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results. The processing of these results is described in a PRISMA flow diagram (**Supplementary material 2**). A first filter of the results by the relevance of the title retained 1,489 references. An effort was made to access the full text of all these references, using in order the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iiI) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details. Unfortunately, 236 references could not be accessed. Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal volumes which had not been digitalised. The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supplementary material 3**) in case they can be processed in the future. The found texts were accessed to retrieve data for the database. At this stage, references were considered to be non-relevant if they (i) did not pertain to species in the original frequent species list; (ii) did not study germination in species monocultures (e.g. competition studies); (iii) did not report the minimal information needed (number of seeds sown, germination percentage and germination temperature). Records were also excluded when they pertained to special germination treatments that do not allow for general comparisons (i.e. use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins). Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supplementary material 4**) and 614 provided relevant data (*BiBTeX* file in **Supplementary material 5**).

## Recording of the database

For each relevant reference, three blocks of information were recorded. The first block described the plant material, including the species, the populations that had been sampled, the year of sampling (or the year of publication if that information was missing), the country, the geographical coordinates (if not provided in the reference, the closest available toponyms were searched in *Google Maps*; in some cases the only geographical information was the country, in these cases the coordinates of the capital were recorded). The second block described the experimental conditions: experimental setting (greenhouse, incubator or room temperature), germination substrate and characteristics of the containers, seed storage, application of seed sterilization or nutrients, length of the germination incubations, use of stratification (none, cold [< 15ºC], warm [>= 15ºC] or combinations of cold and warm), use of scarification, photoperiod, maximum germination temperature, minimum germination temperature, and weighted average germination temperature. The third block contained the final germination proportion: the reported final germination percentages (retrieved from the text, tables or figures) and the reported number of replicates and seeds per replicate were used to calculate a count of seeds sown and a count of seeds germinated.

# Description of the database

## Summary of contents

The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 614 references. The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig. \@ref(fig:fig1)**) in both hemispheres. The oldest record was from `r MSoldest` and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`). There were `r MSspecies` species represented, from `r MSfamilies` seed plant families. The total estimate of seeds used in the experiments was `r MSseeds`. The range of germination temperatures (weighted average of the daily thermoperiod) went from `r MSminT` to `r MSmaxT` ºC, with `r MSaltY` records of constant temperatures and `r MSaltN` of alternating temperatures. Light was used in `r MSlightY` records, darkness in `r MSlightN` and `r MSlightNA` did not provide information on this parameter. The experiments were performed with unstratified seeds in `r MSstratN` records, and of the rest, the majority (`r MSstratCold`) went through cold stratification. Scarification was applied to `r MSscarY` records.

## Database file

The database is provided as a *csv* file, comma separated, named **Supplementary material 6 - Database** (see online supplementary materials). The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Sown_by_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Germinable* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions.

# Sylvan Seeds app

To facilitate the visualization of the database, the *Sylvan Seeds* app was written using the *shiny* package [@RN4661]. It is publicly accessible at http://sylvanseeds.shinyapps.io/sylvanseeds/. The app uses the *tidyverse* package [@RN4662] to aggregate and show results for species and experimental treatments (i.e. aggregating all seed lots of the same species germinated in the same experimental conditions). To facilitate comparisons, germination temperatures are aggregated to 5 ºC intervals. When there is only one seed lot per species and combination of experimental conditions, the binomial 95% confidence interval is calculated using the Wilson method in the *binom* package [@RN2964]. When there is more than one seed lot per species and combination of experimental conditions, the aggregate proportion and binomial confidence intervals are calculated using binomial-normal meta-analysis models [@RN4663] as implemented in the package *metaphor* [@RN2274]. By visiting the app, users can consult the available germination information for a species (**Fig. \@ref(fig:fig2)**), the origin of its seed lots, and the bibliographical references for the species.

# Utility of the database

The database provided in this article, and the web app to visualize it, can have wide applicability in science and beyond. The data can extend current trends in global analyses of plant traits at species [@RN3318] and community levels [@RN4664] to seed germination. The ecological determinants of seed germination are also valuable information for species distribution models [@RN3078]. The visualization of the database with the *Sylvan Seeds* app can help plant ecologists select experimental treatments that are adequate for their experiments [@RN2999]. Outside of academia, the data is useful for seed industries [@RN4665], restoration practitioners [@RN2241] and the implementation of regional schemes for seed-based landscape intervention [@RN4666]. The app is accessible to citizens in general who are interested in germinating wild plants. Finally, apart from the dataset itself, this article can bring two innovations to the seed ecology community, helping to advance the agenda of functional seed ecology [@RN4655]. First, the meta-analysis-inspired methodology used to compile the dataset can be extended to other biomes and lists of species, contributing to the creation of a global database for ecologically and biogeographically coherent floras. Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data.

# References

::: {#refs}
:::

# Data accessibility statement

All persons can use the database providing they cite this data paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as supplementary material and will be stored in *Dryad*. It can be visualized with the *Sylvan Seeds* app at http://sylvanseeds.shinyapps.io/sylvanseeds/. The code of the app is stored at (note: the GitHub page is kept private until publication of the manuscript).

# Figures

```{r fig1, echo = FALSE, fig.pos = "H", fig.cap = "Geographical distribution of the germination records in the database. Each golden circle is a record. The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.", fig.align = "center", fig.width=7, fig.height=3}
p1
```

```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "Example of the germination records as shown by the *Sylvan Seeds* app. Records for one species, the European pedunculate oak, *Quercus robur*. Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel. Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.", fig.align = "center", fig.width=7, fig.height=9}
p2
```

# Appendix 1 – Data sources. List of references used to build the germination database.

**Note: References are provided as they were exported from Web of Science to Endnote, and exactly as they are in the database and the Sylvan Seeds app. They can be edited for final publication.**

```{r echo = FALSE}
MSrefapp
```

### 2020-06-06 app.R

@@ -2,7 +2,7 @@ library(shiny)
 
 library(tidyverse); library(maps); library(here)
 source(here("src", "visualizeDB.R"))
-load(here("data", "appdata.RData"))
+load(here("results", "appdata.RData"))
 spp <- WoSDB %>% select(TPLName) %>% arrange(TPLName) %>% pull(TPLName) %>% unique %>% as.character
 
 # Define UI for application that draws a histogram

### 2020-06-06 src/cleaning.r

@@ -1,0 +1,396 @@
+library(tidyverse); library(here); library(sp); library(openxlsx)
+
+# Cleaning of the search string (Supplementary file 1)
+
+## TPL Names from common source
+
+read.csv("../tpl/results/TPLNames.csv") -> Names
+read.csv("../tpl/results/Families.csv") -> SeedFamilies
+
+## Species file
+
+rbind(
+  read.csv("../splot12/data/Vegetation/species_Edu.csv") %>% 
+    select(PlotObservationID, species, Relative.cover) %>%
+    rename(Cover = Relative.cover, PlotID = PlotObservationID, Taxon = species) %>%
+    mutate(PlotID = paste("Rest", PlotID, sep = "_")),
+  read.csv("../splot12/data/Vegetation/forest2_1500.csv", sep = "\t") %>%
+    select(Relevé.number, Species.name, Cover..) %>%
+    rename(Cover = Cover.., PlotID = Relevé.number, Taxon = Species.name) %>%
+    mutate(PlotID = paste("Japan", PlotID, sep = "_"))) %>%
+  merge(Names, by = "Taxon", all.x = TRUE) %>%
+  filter(Family %in% SeedFamilies$Family) %>%
+  select(PlotID, New.ID, Cover) -> dfSpeciesRevised
+
+## Header file
+
+rbind(
+  read.csv("../splot12/data/Vegetation/TDFNH3_Edu.csv") %>%
+    filter(Herbs.identified..y.n. != "N" | 
+             ! Plants.recorded %in% c("All trees & dominant shrubs", 
+                                      "All woody species", 
+                                      "Dominant woody plants >= 2.5 cm dbh", 
+                                      "Woody plants >= 2.5 cm dbh")) %>%
+    select(PlotObservationID, ECO_NAME, Altitude..m., Aspect..Â.., 
+           Slope..Â.., POINT_X, POINT_Y) %>%
+    rename(PlotID = PlotObservationID, 
+           Ecoregion = ECO_NAME, 
+           Altitude = Altitude..m., 
+           Aspect = Aspect..Â.., 
+           Slope = Slope..Â.., 
+           Longitude = POINT_X, 
+           Latitude = POINT_Y) %>%
+    mutate(PlotID = paste("Rest", PlotID, sep = "_")),
+  
+  read.table("../splot12/data/Vegetation/japan2.txt", sep = ";", header = T) %>%
+    select(PlotID, REALM:ECO_NAME) %>% 
[…]

### 2020-06-06 README.Rmd
readme

---
title: "README.md"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sylvan Seeds

*Sylvan Seeds* is a database of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere. It contains data on >300 plant species, obtained from >600 published references. The data is in the form of germination proportions recorded under experimental combinations of temperature, light, scarification and stratification.

## Contents

The following materials are available in this repository:

* [The database file itself is `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
* [The Sylvan Seeds `shiny` app for visualizing the database](https://sylvanseeds.shinyapps.io/sylvanseeds/)
* The article describing the collection and fields of the database, which is in preparation.

### 2020-06-06 doc/last/last.Rmd
readme

--- 2020-06-06 doc/rev1/rev1.Rmd
@@
 subtitle: "Running title: Sylvan Seeds, a forest germination database"
-output: 
-  bookdown::word_document2:
-    reference_docx: gebtemplate.docx
+output: github_document
 bibliography: refs.bib

### 2020-06-06 README.Rmd
updated readme

@@
 ```
+
+![Sylvan Seeds](data/2017070313 Blue Ridge Parkway small.jpg)
 
@@
 * [The Sylvan Seeds `shiny` app for visualizing the database](https://sylvanseeds.shinyapps.io/sylvanseeds/)
-* The article describing the collection and fields of the database, which is in preparation.
+* [The article describing the collection and fields of the database](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/last/last.md), which is in preparation.
+
+## Citation
+
+Please cite the database as `CITATION`

### 2020-06-06 README.Rmd
readme revised

--- 2020-06-06 README.Rmd
@@
 
+![Sylvan Seeds](data/2017070313 Blue Ridge Parkway small.jpg)
+
 # Sylvan Seeds
 
-*Sylvan Seeds* is a database of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere.
+*Sylvan Seeds* is a dataset of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere.
 It contains data on >300 plant species, obtained from >600 published references.
@@
 
-* [The database file itself is `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
-* [The Sylvan Seeds `shiny` app for visualizing the database](https://sylvanseeds.shinyapps.io/sylvanseeds/)
-* The article describing the collection and fields of the database, which is in preparation.
+* [The dataset file itself is `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
+* [The Sylvan Seeds `shiny` app for visualizing the dataset](https://sylvanseeds.shinyapps.io/sylvanseeds/)
+* [The data paper describing the collection and fields of the dataset](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/last/last.md), which is in preparation.
+
+## Citation
+
+Please cite the dataset as `CITATION`

### 2020-06-21 doc/ms/v2_GEB/response-reviewers.Rmd
NP submission

---
title: "Ref. GEB-2020-0155 - Response to reviewers"
author: "Eduardo Fernández Pascual"
date: "19/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Please, find below my revision of the manuscript. I have considered and applied all suggestions. Considering the major issues, I have (1) expanded the explanation of the chosen biome and the creation of the species list; (2) clarified the missing full texts issue, providing a more detailed description, a PRISMA flow chart, and BibTeX files with the missing references; and (3) expanded the database to include the controlling factors required by the reviewers, such as substrate and number of containers.

# Response to the Editor

> I recommend that the manuscript be rejected with an opportunity to resubmit. The reviewers and myself agreed that the premise of the study was very interesting and relevant to the journal's audience, and appreciate the extensive work that went into its creation. However, a number of issues were identified, which I think preclude publication in present form, and whose resolution would potentially require extensive work on the part of the authors.

> First, the database's content and scope seems broader than warranted by its contents. The first reviewer and I both agree that the data do not necessarily provide full coverage of the proposed biome, and may contain species from beyond it. Additionally, I note that all of the sPlot records used to create a species list are from the Northern hemisphere, when the temperatre / broadleaf forest biome occurs widely in the southern hemisphere. While some of the identified studies end up sourcing data from southern hemisphere sites, it seems inaccurate and overly ambitious to suggest the dataset cover this biome. I am not sure that database with only northern hemisphere coverage of one biome, and with strong biases towards the species and sites represented in sPlot, would be of sufficient interest to receive support in the journal. I encourage the authors to expand the scope of their study, or alternatively provide a robust justification for the current scope, and a clearer title / narrative concomitant with the data.

The editor is right that the biome is also found in the southern hemisphere, although the extension there is smaller than in the northern hemisphere. In the new version of the manuscript, there is a longer explanation of why the NH biome was chosen, and how the species were selected. Summarising, the temperate broadleaf and mixed forests of the Northern Hemisphere were chosen as the subject of a sPlot project. Only the NH was chosen because it forms a coherent biogeographical unit, since it shared a common history during the Tertiary. The SH forests, on the other hand, are separated (and smaller) units and were not connected to the northern forests. This database was created for that specific sPlot project, and it was decided to do so because we expected that the number of germination references would be the highest, since many classical research groups have worked within the NH temperate broadleaf and mixed forests biome. This is developed in more detail in the manuscript and in the response to the reviewers.

In addition, the title has been changed to *Sylvan Seeds, a database and web app to explore the seed germination ecology of temperate broadleaf and mixed forests of the northern hemisphere*.

In any case, and in my personal view, I believe this is the more complete database of raw germination data for a coherent ecological unit and, spanning three continents of a densely populated and significant biome, it has enough global interest for the journal.

> Reviewer #1 also notes that 1/3 of the considered studies were omitted due to access issues; I suggest the authors try to resolve this point, or robustly clarify the justification for this choice. As the manuscript stands currently this text is not very convincing for a reader.

Please see the response to the reviewers about this point.

> Second, the first reviewer identified several issues related to the methodology used for the meta-analysis and literature search. I am sympathetic to these points and suggest the authors revisit their search criteria and data, or provide a robust response to these criticisms.

Please see the response to the reviewers about this point.

> As such, I do not think the data paper is ready to be accepted in present form, but am very willing to consider a thoroughly revised version.

# Responde to Referee 1

> The manuscript describes a dataset of species germination rates where the species were selected based on the sPlot species lists for temperate biomes. The shiny app is a nice addition that could be of use to the broader public with proper dissemination. It is interesting data to compile that will surely be valuable, but the scope of the biomes investigated and a lack of important methodological detail from the germination experiments limits the utility of the data. These concerns and a few others are detailed below.

> I wonder if defining the biome as “temperate broadleaf and mixed forests” is appropriate. There appears to be a number of species that generally occur in grasslands and biomes/habitats outside of forests (e.g. Dactylis glomerata, Achillea millifolium, Festuca ovina, etc.). Did each paper specify that the populations of seed collection were forested? If not, I recommend using something like a Whittaker biome diagram to describe the biomes as temperate rain, deciduous and dry forests, and grass/shrublands. Or just add additional biomes from the WWF classifications.

The new version of the manuscript contains a more detailed explanation of the reason to select the biome, and of the methodology used to construct the list of species. Please see the response to the editor and the manuscript for more comments on this.

The TBMF biome (in the northern hemisphere) is the area which was used to create the list of frequent species, for which the database was then compiled.  Biomes are defined as *relatively large units of land containing a distinct assemblage of natural communities and species, with boundaries that approximate the original extent of natural communities prior to major land-use change*. Thus, the TBMF biome does not contain only forests, but many other habitats such as heathlands, meadows, alpine grasslands, mires, dunes, etc. However, the plots used to create the list were filtered to be only forested plots (i.e., they were selected when they met the criterion that tree species dominated their plant cover). The list that has been produced includes species that occur with high frequency in forested plots of the TBMF biome in the nothern hemisphere. These are trees, shrubs, and herbaceous understory plants adapted to shade. But also species of forest margins, openings, riparian forests, ruderalized forests, etc.

The species mentioned by the reviewer are indeed species of the TBMF biome, and, even if today they may have their optimum in semi-natural meadows and pastures, they can occur also in forested plots (and in fact they do, as sown by the vegetation relevés we used). *Dactylis glomerata* and *Achillea millifolium* are species of mesic meadows (*Molinio-Arrhenatheretea*), which are secondary communities developped by human intervention over habitats that would be naturally occupied by temperate forests. The traditional interpretation of the origin of these communities is that they originated in forest margin communities that colonized the openings created by humans. Therefore, it is not surprising that these species are recorded with relative frequency in forest plots, as indeed they are. Similarly, it is not surprising that dry grassland (*Festuco-Brometea*) species such as *Festuca ovina* are also recorded in forest plots, especially in contact areas, as these are also communities that expanded over landscapes that would naturally be forests.

I agree that the seed lot coordinates that are provided with the database could be used to construct a Whittaker diagram of the seed lots, or alternatively to asign them to WWF biomes. But I feel that this is more of an analytical usage of the data, which can be done by any user with the information provided in the dataset. Still, I am willing to do such tasks if the editor finds them essential.

> The justification for restricting the search to certain biomes and species is weak (Lines 49-50), especially given sPlot is a global database. If picking these biomes covers most of the available data, why not extend beyond this biome given the added work is relatively minimal? Then the dataset would be truly global. There are a lot of papers on germination outside of this biome that could make for valuable comparisons (e.g., tundra/alpine biomes from Vandvik et al. 2017. Botany 95:73-88; Tropical forests from Yu et al. 2008. Plant Ecology 297:1-16). Why not expand the search to all species within sPlot? If the search is expanded to all species in sPlot, does the number of articles requiring processing become unreasonable? This would make for a better justification for restricting the search.

I have included a more detailed description of the reasons behind chosing the TBMF biome to construct the database: *The building of the dataset was part of a research project conducted within the sPlot initiative (Bruelheide et al., 2019), specifically sPlot’s project #12 (https://www.idiv.de/en/sdiv/working_groups/wg_pool/splot/projects.html). The goal of sPlot #12 was to study taxonomical and functional plant diversity in deciduous forests, which are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers. In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe (Milne & Abbott, 2002).*

Completing the database for all the species in sPlot is a worthwhile long-term goal (as mentioned in the *Utility of the database* section of the manuscript), and one that I am interested in contributing to in the future. But it was completely beyond the resources I had to construct this database, which depended on a 2-year personal grant. It took me 9 months of focused work to build a database for 1,393 species. There are 54,519 species in sPlot 2.1 (*Bruelheide, H., Dengler, J., Jiménez‐Alfaro, B., Purschke, O., Hennekens, S. M., Chytrý, M., ... & Aubin, I. (2019). sPlot–A new tool for global vegetation analyses. Journal of Vegetation Science, 30(2), 161-186*). Therefore, a rough estimate is that it would take me 29 years of work to do a database for all sPlot species! Even if the time would probably be shorter (because I do expect the number of references would be lower outside the TBMF biome), the number of references would be expanding each year with new research. So, because one has to start somewhere, I chose to do it in connection to sPlot project 12, which focused on temperate broadleaf and mixed forests of the northern hemisphere; and I chose to do it because this biome has received much attention in seed research.

> The literature search would benefit from more description and/or investigation. What made a full text impossible to access? Not having access to a few full texts is understandable, but 236 would make up more than 1/3 of the 611 that were to be relevant. This data could be very important to the completeness of the dataset. Using PRISMA guidelines for proper meta-analysis data gather is highly recommended (http://www.prisma-statement.org).

Just to be precise, the proportion of not-found information is actually smaller. Of 1489 references for which I searched for the full text, I found 1253 (NOTE: While doing the revisions, I have found and corrected small discrepancies in the numbers of references, caused because a few of the records were removed by a mismatch during taxon name standardization). Of these, 639 (51%) were not relevant. If we assume the same proportion of relevant references in the cases for which I could not find the full text, we can estimate that there were 116 relevant articles which I could not include in the database: 16% of the potentially relevant references (614 found + 116 estimated not found = 730; 116/730 =  0.16). Furthermore, I must note that information is not homogenesouly distributed thorough the references: there are many references for some popular species, and fewer references for rarer species. Therefore the amount of valuable information does not increase linearly with increasing number of references, and it is very likely that a large proportion of that 16% is made up of references considering species which are already in the database. In conclusion, I believe that the amount of missing information is within reasonable limits.

Be that as it may, I have improved the description of data gathering in the text, including a description of the process of finding full texts: *An effort was made to access the full text of all these references, using in order the following channels: (i) “Find Full Text” functionality in EndNote X9, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iiI) request to the authors through ResearchGate; (iv) general search of pdf files in Google using the article details. Unfortunately, 236 references could not be accessed. Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal volumes which had not been digitalised.*

I have also included some supplementary materials to describe the data gathering: the boolean search string I used in the Web of Science, and a PRISMA flow chart.

Additionally, I have added the lists of the three types of references (non-relevant, found and not-found) as BibTeX supplementary files. In this way, it will be possible to check what I did, and to complete it in the future by accessing the references that I could not find.

> There appears to be a lot of important information missing in the dataset that would allow a user of the dataset to control for methodological artifacts or biases. For example: what kind of substrate were the seeds germinated in (Agar? Soil? Sand?)? What was the density of seeds sown? How large were the containers holding the seeds? How many replicates were there to determine the number germinated versus germinable? Were any treatments, such as drought or nutrient addition, used in the experiment? Were the seeds sown in a monoculture?

As requested, I have revised the references to retrieve the requested information, and added it to the database: type of substrate; type and dimensions of the containers; number of containers and number of seeds sown per container; treatments of sterilization and nutrients. Density of seeds is not reported in the references, but it can be estimated from the dimension of the containers and the number of seeds sown. All cases included in the database correspond to monoculture experiments, and special treatments (drought, heavy meatals, smoke, etc.) were not included; this is now stated in the text. Please see the manuscript for the description of the new variables in the database.

> Most of the studies would have replicated germination trials (e.g. sown 100 seeds across 5 replicates: 20 seeds per replicate). Therefore, there is likely true error estimates (and mean percent germination) that can be obtained from the papers. These are a highly desirable metrics from the papers and would improve the error estimates in the shiny app as well.

As requested, I have included the number of containers ("replicates") and number of seeds sown per replicate in the database.

> Line 12- add an “and” so that it reads “darkness, and constant or alternating”

Done.

> Line 16- Will the data collection be continuous? Maybe assign a final year here.

Done.

> Line 31- add an of; “all of these”

Done.

> Line 35- use commas instead of –

Done.

> Line 39-40- “which implies a set of derived complications in the analytical treatment of the data”- unclear what this means and how it applies to germination as a number of successes given seeds sown (trials).

I have removed the whole sentence.

> Line 45- Rather than “at this and that temperature”, try “across a temperature gradient”?

Done.

> Line 95- give a brief explanation of GA3

Done.

> Line 104-105- Remove highlight of Fig. 1.

Done.

> Line 108- incorrect degree symbol.

It was the degree symbol rendered in the Calibri font, the new manuscript is in Arial.

> Line 154- remove the “a” to read “can have wide applicability”

Done.

> Line 155-157- Try “The data can extend current trends in global analyses of plant traits at species (Diaz et al., 2016) and community levels (Bruelheide t al., 2018) to seed germination.”

Done.

> Line 160- Remove “to”

Done.

> Line 262- As the authors note, the references will need cleaning.

Indeed.

> Can the species names be searchable in addition to the drop-down menu in the shiny app?

The species name can be deleted, and then one can write in the box. This will trigger an autocomplete, which will allow to search.

> There are special character errors in the “Reference” column of the dataset: e.g., «ali?kan, O., et al. (2012). "Influences of presowing treatments on the germination and emergence of fig seeds (Ficus carica L.)." Acta Scientiarum. Agronomy 34(3): 293-297.

This should be fixed now.

# Responde to Referee 2

> This data paper introduces a new resource available to ecologists: a data base and associated app summarising seed germination data for a large number of plant species in the temperate broadleaf/mixed forest biome. The authors used an extensive literature search to identify sources of germination data, and have gone through a substantial effort in extracting data from a large number of published articles. The resulting ‘Sylvan Seeds’ data base and app has the potential to be a valuable tool for researchers and applied foresters. I had a quick play around with the app – it provides nice species-specific data summaries (although I think the data base itself is going to be a more useful resource).

> I have little to criticise in terms of the approaches used (which seem sound), but believe that the presentation would benefit from a few changes to make it more reader friendly and accessible for people whose main interest might not be in seed ecology and to potential non-academic users of the database/app:

> L1 (Title): I am not sure how many people will immediately know what a ‘shiny app’ is. (I did not...) Could another more general term be used?

I changed it to *web app*.

> L5 (Motivation): This section could perhaps start with a sentence on why seed germination is an important phenomenon in ecology?

Done.

> L9-10: “Data has been gathered using a meta-analytical approach to search the literature.” Meta-analytical approach may suggest that some kind of data analysis was involved. Could be changed to something along the lines of “Data were gathered using a systematic literature search approach” or similar. (Later in the text you could then mention that the exact approach taken was inspired by approaches typically used in meta-analyses?)

Changed as suggested.

> L14: “across the biome and beyond” – unclear meaning

Changed to *Seed lots collected throughout the biome and in neighbouring areas*.

> L16: today -> March 2019?

Changed to the year of the most recent seed lot, 2017.

> L17: frequent -> common?

I believe it is more appropiate to use frequent, as frequency is the common term in plant ecology: *Frequency is the number of times a plant species occurs in a given number of quadrats*. Frequency, thus defined, was the criterion used to include species in the search.

> L20: wide -> wider?

Changed.

> L25: Again, considering the broad readership of Global Ecology and Biogeography, it might be helpful to start with a sentence or two on the importance of studying seed traits/germination/seed ecology (and – given the journal – ideally also something on why a global approach can contribute to the field of seed ecology).

Done.

> L41: scarcity of -> lack of? (Alternatively, if such data bases exist, but there are only few of them, stick to original wording but mention which ones exist.)

Changed to *lack of*.

> L45: at this and that temperature -> at various temperatures

Changed to *accross a temperature gradient* as suggested by referee 1.

> L49-50: home of many of the classical research groups in seed ecology -> research focus of (…) or similar?

Changed to *At the same time, a relatively high number of classic seed biology research groups have worked within the TBMFNH areas, e.g. in the USA (Baskin, 1995), the UK (Grime et al., 1981), Belgium (Van Assche & Vandelook, 2006) and Japan (Washitani, 1988). *.

> L51: see previous comment regarding reference to meta-analysis

Changed to *To gather data for the project, a systematic literature search (Koricheva et al., 2013) was applied to a list of frequent species representing the flora of the TBMFNH.*

> L57: not all readers might be familiar with the term vegetation relevé -> provide brief explanation?

The following explanation has been added: *(i.e. records of plant species co-occurring in a sampling plot)*

> L58: the reference to sPlot’s project #12 might not mean much to people not involved with sPlot. -> Provide link to website or further explanation?

I have included the following description: *The building of the dataset was part of a research project conducted within the sPlot initiative (Bruelheide et al., 2019), specifically sPlot’s project #12 (https://www.idiv.de/en/sdiv/working_groups/wg_pool/splot/projects.html). The goal of sPlot #12 was to study taxonomical and functional plant diversity in deciduous forests, which are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers. In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe (Milne & Abbott, 2002).*. Unfortunately, no articles derived from sPlot #12 have been finished so far, so I cannot cite them, which would be the ideal solution.

> L72: ‘To obtain a final list of species (…)’. The primary reason for focusing on the subset of species that were present in a minimum of 5% of the relevés of an ecoregion was presumably to make the work achievable given the large number of species (>7000) in the full species pool?

There was the practical reason mentioned by the reviewer, but also a methodological consideration. I have added the following explanation: *There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of TBMFNH, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.).*

> L81-82: “(…) for 236 it was impossible to access the full text.” Unclear meaning: Was this because of lack of institutional licenses for accessing journals, or because of something else?

Please see the response to referee 1 about the same question. The causes are now described as follows: *An effort was made to access the full text of all these references, using in order the following channels: (i) “Find Full Text” functionality in EndNote X9, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iiI) request to the authors through ResearchGate; (iv) general search of pdf files in Google using the article details. Unfortunately, 236 references could not be accessed. Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal volumes which had not been digitalised.*.

> L95: GA3 -> gibberellic acid (to help readers who are less familiar with the topic, could perhaps also mention that GA3 speeds up seed germination)

Done.

> L96: the term ‘response variable’ suggests that you conducted some kind of statistical analysis. -> Delete term or change wording.

Removed *the response variable* part of the sentence.

### 2020-06-21 doc/ms/v3_NewPhytol/cover-letter.Rmd
NP submission

---
title: "Cover letter"
author: "Eduardo Fernández Pascual"
date: "20/6/2020"
output: pdf_document
bibliography: refs.bib
csl: new-phytologist.csl
link-citations: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dear Editorial Board,

I submit my manuscript *SylvanSeeds, a database and web app to explore seed germination in temperate broadleaf and mixed forests* to be considered for publication as a **Methods** paper in New Phytologist.

## What hypotheses or questions does this work address?

This is a methods paper describing *SylvanSeeds*, a database and web app (http://sylvanseeds.shinyapps.io/sylvanseeds/) of raw germination records for frequent species of temperate deciduous and mixed forests. The list of frequent species was created using 17,852 vegetation relevés from the sPlot database [@RN4658].

## How does this work advance our current understanding of plant science?

*SylvanSeeds* makes publicly available 4,828 germination records of 364 species from 74 families, collected in 46 countries between 1920-2017. The database is the result of a systematic literature search that screened 6,791 references and extracted raw data from 614. This manuscript presents the search methodology, applicable to other biomes.

## Why is this work important and timely?

Plant science is embarked on a global synthesis of functional traits at species [@RN3318] and community levels [@RN4664]. Synthesis of seed functions is however hindered by a lack of global germination datasets [@RN4655], a gap filled by *SylvanSeeds*.

## References

### 2020-06-21 doc/ms/v3_NewPhytol/ms.Rmd
NP submission

--- 2020-06-06 doc/last/last.Rmd
@@
 ---
-title: "Sylvan Seeds, a database and web app to explore the seed germination ecology of temperate broadleaf and mixed forests of the northern hemisphere"
-subtitle: "Running title: Sylvan Seeds, a forest germination database"
-output: github_document
+title: "SylvanSeeds, a database and web app to explore seed germination in temperate broadleaf and mixed forests"
+subtitle: "Running title: SylvanSeeds, a forest germination database"
+output: 
+  bookdown::word_document2:
+    reference_docx: template.docx
 bibliography: refs.bib
-csl: global-ecology-and-biogeography.csl
+csl: new-phytologist.csl
 link-citations: yes
@@
 
-# Abstract
+**Author:** Eduardo Fernández-Pascual **Institutional address:** Departamento de Biología de Organismos y Sistemas, Universidad de Oviedo, C/ Catedrático Rodrigo Uría, 33006 Oviedo/Uviéu, Spain **Email:** efernandezpascual@gmail.com **Telephone:** +34985104787
 
-*Motivation* Seed traits have functional significance in all levels of plant ecology, from population dynamics to community assembly and species distribution models.
-Recent discussions on the utility of seed traits in ecology have highlighted the unavailability of reliable germination databases of wide geographical scope.
-This data paper presents a first global dataset of raw germination data, encompassing an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere.
-Data were gathered using a systematic literature search approach.
+**Total word count** 2,578 **Introduction** 530 **Materials and Methods** 968 **Results** 848 **Discussion** 226 **Number of figures** 2 in colour **Tables** 0 **Supporting information** 6
 
-*Main types of variable contained* Proportion of seeds germinated in laboratory experiments, under different experimental combinations of scarification, stratification, light or darkness, and constant or alternating germination temperatures.
+# Summary
 
-*Spatial location and grain* Seed lots collected throughout the biome and in neighbouring areas, with approximate geographical coordinates of the collecting sites.
+* Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope.
+This article presents *SylvanSeeds*, a first global dataset of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests.
 
-*Time period and grain* Seed lots collected between 1920 and 2017.
+* Data were gathered with a systematic literature search.
+A list of frequent taxa of the study area was created using `r MSplots` vegetation relevés from the sPlot database.
+The list was searched in the Web of Science.
+6,791 references were screened, finding 614 articles from which data were extracted.
 
-*Major taxa and level of measurement* 326 plant species with high frequency in vegetation relevés of the biome, representing 74 families of seed plants (gymnosperms and angiosperms).
+* *SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017.
+It provides raw data for meta-analysis: proportions of seeds germinated in laboratory experiments of scarification, stratification, light-darkness, and constant-alternating temperatures.
+*SylvanSeeds* is freely distributed as a *.csv*.
+The shiny app *SylvanSeeds* is also presented, to make data accessible to the public.
 
-*Software format* The database is provided as a single *.csv* file. The shiny web app *Sylvan Seeds* is also presented, to explore the database and make it accessible to the wider public.
+* *SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.
+First, the data-gathering methodology can be extended to other biomes.
+Second, database and app can be a standard in further efforts to compile germination data.
 
-# Keywords
-
-Temperate deciduous forests, temperate evergreen forests, temperate coniferous forests, seed traits, germination database, seed dormancy, germination temperature, alternating temperatures, light germination, dark germination
+**Keywords:** germination database, germination temperature, light and dark germination, seed dormancy, seed traits, temperate coniferous forests, temperate deciduous forests, temperate evergreen forests
 
@@
 
-Seed traits have functional significance in all levels of plant ecology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942].
-Recent discussions [@RN2352; @RN4655] highlighted the unavailability of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum.
-Seed germination is the first major developmental transition in the life of a plant, and as such it has profound effects on the plant's ecology [@RN2384].
+Seed traits have functional significance in all levels of plant biology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942].
+Recent discussions [@RN2352; @RN4655] highlighted the lack of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum.
+Seed germination is the first major developmental transition in the life of a plant, and it has profound effects on the plant's ecology [@RN2384].
 As such, the timing of this transition is controlled by a combination of environmental signals.
@@
 
-To fill this gap, this data paper presents a first global dataset of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*).
+To fill this gap, this article presents *SylvanSeeds*, a first global dataset of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*).
 The building of the dataset was part of a research project conducted within the *sPlot* initiative [@RN4658], specifically *sPlot*’s project #12 (https://www.idiv.de/en/sdiv/working_groups/wg_pool/splot/projects.html).
@@
 This data paper makes the database accessible to the research community.
-Additionally, the *Sylvan Seeds* shiny web app is presented to facilitate the exploration of the data.
+Additionally, the *SylvanSeeds* shiny web app is presented to facilitate the exploration of the data.
 
-# Methods
+# Materials and Methods
 
@@
 
-The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)” (**Supplementary material 1**).
+The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)” (**Supporting Information 1**).
 This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results.
-The processing of these results is described in a PRISMA flow diagram (**Supplementary material 2**).
+The processing of these results is described in a PRISMA flow diagram (**Supporting Information 2**).
 A first filter of the results by the relevance of the title retained 1,489 references.
-An effort was made to access the full text of all these references, using in order the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iiI) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details.
+An effort was made to access the full text of all these references, using in order the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iii) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details.
 Unfortunately, 236 references could not be accessed.
 Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal volumes which had not been digitalised.
-The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supplementary material 3**) in case they can be processed in the future.
+The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supporting Information 3**) in case they can be processed in the future.
 The found texts were accessed to retrieve data for the database.
@@
 use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins).
-Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supplementary material 4**) and 614 provided relevant data (*BiBTeX* file in **Supplementary material 5**).
+Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supporting Information 4**) and 614 provided relevant data (*BiBTeX* file in **Supporting Information 5**).
 
@@
 
-# Description of the database
+# Results
 
@@
 \@ref(fig:fig1)**) in both hemispheres.
-The oldest record was from `r MSoldest` and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`).
+The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`).
 There were `r MSspecies` species represented, from `r MSfamilies` seed plant families.
@@
 
-The database is provided as a *csv* file, comma separated, named **Supplementary material 6 - Database** (see online supplementary materials).
+The database is provided as a *csv* file, comma separated, named **Supporting Information 6** (see online Supporting Information).
 The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Sown_by_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Germinable* (count of seeds used in the experiment).
 Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions.
+Presenting the response variable as a proportion (i.e.
+number of successes *Germinated*, number of trials *Germinable*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].
 
-# Sylvan Seeds app
+## SylvanSeeds app
 
-To facilitate the visualization of the database, the *Sylvan Seeds* app was written using the *shiny* package [@RN4661].
+To facilitate the visualization of the database, the *SylvanSeeds* app was written using the *shiny* package [@RN4661].
 It is publicly accessible at http://sylvanseeds.shinyapps.io/sylvanseeds/.
@@
 When there is only one seed lot per species and combination of experimental conditions, the binomial 95% confidence interval is calculated using the Wilson method in the *binom* package [@RN2964].
-When there is more than one seed lot per species and combination of experimental conditions, the aggregate proportion and binomial confidence intervals are calculated using binomial-normal meta-analysis models [@RN4663] as implemented in the package *metaphor* [@RN2274].
+When there is more than one seed lot per species and combination of experimental conditions, the aggregate proportion and binomial confidence intervals are calculated using binomial-normal meta-analysis models [@RN4663] as implemented in the package *metafor* [@RN2274].
 By visiting the app, users can consult the available germination information for a species (**Fig.
@@
 
-# Utility of the database
+# Discussion
 
 The database provided in this article, and the web app to visualize it, can have wide applicability in science and beyond.
-The data can extend current trends in global analyses of plant traits at species [@RN3318] and community levels [@RN4664] to seed germination.
+It can extend current trends in global analyses of plant traits at species [@RN3318] and community levels [@RN4664] to seed germination.
 The ecological determinants of seed germination are also valuable information for species distribution models [@RN3078].
-The visualization of the database with the *Sylvan Seeds* app can help plant ecologists select experimental treatments that are adequate for their experiments [@RN2999].
-Outside of academia, the data is useful for seed industries [@RN4665], restoration practitioners [@RN2241] and the implementation of regional schemes for seed-based landscape intervention [@RN4666].
+The visualization of the database with the *SylvanSeeds* app can help plant ecologists select experimental treatments that are adequate for their experiments [@RN2999].
+Outside of academia, germination data are useful for seed industries [@RN4665], restoration practitioners [@RN2241] and the implementation of regional schemes for seed-based landscape intervention [@RN4666].
 The app is accessible to citizens in general who are interested in germinating wild plants.
@@
 Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data.
+
+# Acknowledgements
+
+E.F.P.
+received financial support from the Government of Asturias and the FP7 – Marie Curie - COFUND programme of the European Commission (Grant ‘Clarín’ ACB17-19).
+The list of species was built thanks to sPlot, a project of the Synthesis Centre of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.
+
+# Author Contribution
+
+This is a single-author article.
 
@@
 
-# Data accessibility statement
+# Supporting Information
 
-All persons can use the database providing they cite this data paper properly in any publications or in the metadata of any derived products that are produced using the database.
-The database is provided as supplementary material and will be stored in *Dryad*.
-It can be visualized with the *Sylvan Seeds* app at http://sylvanseeds.shinyapps.io/sylvanseeds/.
-The code of the app is stored at (note: the GitHub page is kept private until publication of the manuscript).
+**Supporting Information 1** Boolean search string used in the Web of Science.
+**Supporting Information 2** PRISMA 2009 flow chart describing the process of reference screening and inclusion.
+**Supporting Information 3** BibTeX bibliography listing the not found full texts.
+**Supporting Information 4** BibTeX bibliography listing the non-relevant references.
+**Supporting Information 5** BibTeX bibliography listing relevant references included in the *SylvanSeeds* database.
+**Supporting Information 6** *SylvanSeeds* database in a single *.csv* file.
+
+# Data accessibility
+
+All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
+The database is provided as Supporting Information.
+It can be visualized with the *SylvanSeeds* app at http://sylvanseeds.shinyapps.io/sylvanseeds/.
+The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).
 
@@
 
-```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "Example of the germination records as shown by the *Sylvan Seeds* app.
+```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "Example of the germination records as shown by the *SylvanSeeds* app.
 Records for one species, the European pedunculate oak, *Quercus robur*.
@@
 ```
-
-# Appendix 1 – Data sources. List of references used to build the germination database.
-
-**Note: References are provided as they were exported from Web of Science to Endnote, and exactly as they are in the database and the Sylvan Seeds app. They can be edited for final publication.**
-
-```{r echo = FALSE}
-MSrefapp
-```

### 2020-06-21 src/NewPhytol figures.R

@@ -1,0 +1,9 @@
+library(tidyverse); library(here)
+
+load(file = here("results", "msfigs.RData"))
+
+ggsave(p1, file = here("doc", "ms", "v3_NewPhytol", "Fig1.png"), 
+       path = NULL, scale = 1, width = 150, height = 80, units = "mm", dpi = 600)
+
+ggsave(p2, file = here("doc", "ms", "v3_NewPhytol", "Fig2.png"), 
+         path = NULL, scale = 1, width = 150, height = 160, units = "mm", dpi = 600)

### 2020-06-21 src/cleaning.r

@@ -4,17 +4,17 @@ library(tidyverse); library(here); library(sp); library(openxlsx)
 
 ## TPL Names from common source
 
-read.csv("../tpl/results/TPLNames.csv") -> Names
-read.csv("../tpl/results/Families.csv") -> SeedFamilies
+read.csv("../#tpl/results/TPLNames.csv") -> Names
+read.csv("../#tpl/results/Families.csv") -> SeedFamilies
 
 ## Species file
 
 rbind(
-  read.csv("../splot12/data/Vegetation/species_Edu.csv") %>% 
+  read.csv("../#plots/data/sPlot12/species_Edu.csv") %>% 
     select(PlotObservationID, species, Relative.cover) %>%
     rename(Cover = Relative.cover, PlotID = PlotObservationID, Taxon = species) %>%
     mutate(PlotID = paste("Rest", PlotID, sep = "_")),
-  read.csv("../splot12/data/Vegetation/forest2_1500.csv", sep = "\t") %>%
+  read.csv("../#plots/data/sPlot12/forest2_1500.csv", sep = "\t") %>%
     select(Relevé.number, Species.name, Cover..) %>%
     rename(Cover = Cover.., PlotID = Relevé.number, Taxon = Species.name) %>%
     mutate(PlotID = paste("Japan", PlotID, sep = "_"))) %>%
@@ -25,7 +25,7 @@ rbind(
 ## Header file
 
 rbind(
-  read.csv("../splot12/data/Vegetation/TDFNH3_Edu.csv") %>%
+  read.csv("../#plots/data/sPlot12/TDFNH3_Edu.csv") %>%
     filter(Herbs.identified..y.n. != "N" | 
              ! Plants.recorded %in% c("All trees & dominant shrubs", 
                                       "All woody species", 
@@ -42,9 +42,9 @@ rbind(
            Latitude = POINT_Y) %>%
     mutate(PlotID = paste("Rest", PlotID, sep = "_")),
   
-  read.table("../splot12/data/Vegetation/japan2.txt", sep = ";", header = T) %>%
+  read.table("../#plots/data/sPlot12/japan2.txt", sep = ";", header = T) %>%
     select(PlotID, REALM:ECO_NAME) %>% 
-    merge(read.csv("../splot12/data/Vegetation/forest2_1500.hea", sep = "\t", quote = ""), by = "PlotID") %>%
[…]

### 2020-06-30 doc/ms/v4_JVS/cover-letter.Rmd
JVS submission

--- 2020-06-21 doc/ms/v3_NewPhytol/cover-letter.Rmd
@@
 title: "Cover letter"
-author: "Eduardo Fernández Pascual"
+author: "Eduardo Fernández-Pascual"
 date: "20/6/2020"
@@
 bibliography: refs.bib
-csl: new-phytologist.csl
+csl: journal-of-vegetation-science.csl
 link-citations: yes
@@
 
-I submit my manuscript *SylvanSeeds, a database and web app to explore seed germination in temperate broadleaf and mixed forests* to be considered for publication as a **Methods** paper in New Phytologist.
+I submit my manuscript *SylvanSeeds, a seed germination database for temperate deciduous forests* to be considered for publication as a **Report** in the Journal of Vegetation Science.
+This is a first submission to JVS and it comprises work that has not been published, and is not being considered for publication elsewhere.
 
-## What hypotheses or questions does this work address?
-
-This is a methods paper describing *SylvanSeeds*, a database and web app (http://sylvanseeds.shinyapps.io/sylvanseeds/) of raw germination records for frequent species of temperate deciduous and mixed forests.
+This report describes *SylvanSeeds*, a database and web app (https://efernandezpascual.shinyapps.io/sylvanseeds/) of raw germination records for frequent species of temperate broadleaf and mixed forests.
 The list of frequent species was created using 17,852 vegetation relevés from the sPlot database [@RN4658].
-
-## How does this work advance our current understanding of plant science?
 
@@
 
-## Why is this work important and timely?
-
 Plant science is embarked on a global synthesis of functional traits at species [@RN3318] and community levels [@RN4664].

### 2020-06-30 doc/ms/v4_JVS/ms.Rmd
JVS submission

--- 2020-06-21 doc/ms/v3_NewPhytol/ms.Rmd
@@
 ---
-title: "SylvanSeeds, a database and web app to explore seed germination in temperate broadleaf and mixed forests"
+title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
 subtitle: "Running title: SylvanSeeds, a forest germination database"
@@
 
-**Total word count** 2,578 **Introduction** 530 **Materials and Methods** 968 **Results** 848 **Discussion** 226 **Number of figures** 2 in colour **Tables** 0 **Supporting information** 6
+# Abstract
 
-# Summary
-
-* Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope.
-This article presents *SylvanSeeds*, a first global dataset of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests.
-
-* Data were gathered with a systematic literature search.
+Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope.
+This article presents *SylvanSeeds*, a first global database of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests.
+Data were gathered with a systematic literature search.
 A list of frequent taxa of the study area was created using `r MSplots` vegetation relevés from the sPlot database.
@@
 6,791 references were screened, finding 614 articles from which data were extracted.
-
-* *SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017.
+*SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017.
 It provides raw data for meta-analysis: proportions of seeds germinated in laboratory experiments of scarification, stratification, light-darkness, and constant-alternating temperatures.
 *SylvanSeeds* is freely distributed as a *.csv*.
-The shiny app *SylvanSeeds* is also presented, to make data accessible to the public.
-
-* *SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.
+The shiny app *SylvanSeeds* (https://efernandezpascual.shinyapps.io/sylvanseeds/) is also presented, to make data accessible to the public.
+*SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.
 First, the data-gathering methodology can be extended to other biomes.
@@
 
-**Keywords:** germination database, germination temperature, light and dark germination, seed dormancy, seed traits, temperate coniferous forests, temperate deciduous forests, temperate evergreen forests
+**Keywords:** germination database, germination temperature, light and dark germination, seed dormancy, seed traits, temperate coniferous forests, temperate broadleaf and mixed forests, temperate evergreen forests
 
@@
 
-Seed traits have functional significance in all levels of plant biology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942].
+Seed traits have functional significance in all levels of plant ecology, from population dynamics [@RN3043] to community assembly [@RN2942] and species distributions [@RN2942].
 Recent discussions [@RN2352; @RN4655] highlighted the lack of reliable germination databases of wide geographical scope as a major limitation to produce a global synthesis of the seed ecological spectrum.
@@
 
-To fill this gap, this article presents *SylvanSeeds*, a first global dataset of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*).
-The building of the dataset was part of a research project conducted within the *sPlot* initiative [@RN4658], specifically *sPlot*’s project #12 (https://www.idiv.de/en/sdiv/working_groups/wg_pool/splot/projects.html).
-The goal of *sPlot* #12 was to study taxonomical and functional plant diversity in deciduous forests, which are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers.
+To fill this gap, this article presents *SylvanSeeds*, a first global database of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*).
+Deciduous forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers.
 In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe [@RN4684].
@@
 in the USA [@RN1045], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188].
-For this reason, *sPlot* project #12 was chosen to incorporate a biome-wide analysis of seed traits, as it was expected that the *TBMFNH* would provide a wide scope of available data.
-To gather data for the project, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the *TBMFNH*.
-This data paper makes the database accessible to the research community.
+To create *SylvanSeeds*, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the *TBMFNH*.
+This article makes the database accessible to the research community.
 Additionally, the *SylvanSeeds* shiny web app is presented to facilitate the exploration of the data.
@@
 
-The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)” (**Supporting Information 1**).
+The list of frequent species (plus the synonyms recorded in the relevés) was incorporated into a Boolean search string, together with the words "(seed OR seeds) AND (dormancy OR germination)”.
 This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results.
-The processing of these results is described in a PRISMA flow diagram (**Supporting Information 2**).
+The processing of these results is described in a PRISMA flow diagram (**Supporting Information 1**).
 A first filter of the results by the relevance of the title retained 1,489 references.
-An effort was made to access the full text of all these references, using in order the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iii) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details.
+An effort was made to access the full text of all these references, using the following channels: (i) “Find Full Text” functionality in *EndNote X9*, (ii) online access to the journals using the institutional subscriptions of the University of Oviedo; (iii) request to the authors through *ResearchGate*; (iv) general search of *pdf* files in *Google* using the article details.
 Unfortunately, 236 references could not be accessed.
-Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal volumes which had not been digitalised.
-The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supporting Information 3**) in case they can be processed in the future.
+Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal issues which had not been digitalised.
+The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supporting Information 2**) in case they can be processed in the future.
 The found texts were accessed to retrieve data for the database.
@@
 use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins).
-Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supporting Information 4**) and 614 provided relevant data (*BiBTeX* file in **Supporting Information 5**).
+Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supporting Information 3**) and 614 provided relevant data (*BiBTeX* file in **Supporting Information 4**).
 
@@
 For each relevant reference, three blocks of information were recorded.
-The first block described the plant material, including the species, the populations that had been sampled, the year of sampling (or the year of publication if that information was missing), the country, the geographical coordinates (if not provided in the reference, the closest available toponyms were searched in *Google Maps*; in some cases the only geographical information was the country, in these cases the coordinates of the capital were recorded).
+The first block described the plant material, including the species, the populations that had been sampled, the year of sampling (or the year of publication if that information was missing), the country, the geographical coordinates (if not provided in the reference, the closest available toponyms were searched in *Google Maps*; in some cases the only geographical information was the country, in these cases the coordinates of the capital city were recorded).
 The second block described the experimental conditions: experimental setting (greenhouse, incubator or room temperature), germination substrate and characteristics of the containers, seed storage, application of seed sterilization or nutrients, length of the germination incubations, use of stratification (none, cold [< 15ºC], warm [>= 15ºC] or combinations of cold and warm), use of scarification, photoperiod, maximum germination temperature, minimum germination temperature, and weighted average germination temperature.
@@
 The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig.
-\@ref(fig:fig1)**) in both hemispheres.
+\@ref(fig:fig1)**), in both hemispheres.
 The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`).
@@
 
-The database is provided as a *csv* file, comma separated, named **Supporting Information 6** (see online Supporting Information).
+The database is provided as a *csv* file, comma separated, named **Supporting Information 5** (see online Supporting Information).
 The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Sown_by_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Germinable* (count of seeds used in the experiment).
@@
 To facilitate the visualization of the database, the *SylvanSeeds* app was written using the *shiny* package [@RN4661].
-It is publicly accessible at http://sylvanseeds.shinyapps.io/sylvanseeds/.
+It is publicly accessible at https://efernandezpascual.shinyapps.io/sylvanseeds/.
 The app uses the *tidyverse* package [@RN4662] to aggregate and show results for species and experimental treatments (i.e.
@@
 The app is accessible to citizens in general who are interested in germinating wild plants.
-Finally, apart from the dataset itself, this article can bring two innovations to the seed ecology community, helping to advance the agenda of functional seed ecology [@RN4655].
-First, the meta-analysis-inspired methodology used to compile the dataset can be extended to other biomes and lists of species, contributing to the creation of a global database for ecologically and biogeographically coherent floras.
+Finally, apart from the database itself, this article can bring two innovations to the seed ecology community, helping to advance the agenda of functional seed ecology [@RN4655].
+First, the meta-analysis-inspired methodology used to compile the database can be extended to other biomes and lists of species, contributing to the creation of a global database for ecologically and biogeographically coherent floras.
 Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data.
@@
 
-# Author Contribution
-
-This is a single-author article.
-
 # References
@@
 
-**Supporting Information 1** Boolean search string used in the Web of Science.
-**Supporting Information 2** PRISMA 2009 flow chart describing the process of reference screening and inclusion.
-**Supporting Information 3** BibTeX bibliography listing the not found full texts.
-**Supporting Information 4** BibTeX bibliography listing the non-relevant references.
-**Supporting Information 5** BibTeX bibliography listing relevant references included in the *SylvanSeeds* database.
-**Supporting Information 6** *SylvanSeeds* database in a single *.csv* file.
+**Supporting Information 1** PRISMA 2009 flow chart describing the process of reference screening and inclusion.
+**Supporting Information 2** BibTeX bibliography listing the not found full texts.
+**Supporting Information 3** BibTeX bibliography listing the non-relevant references.
+**Supporting Information 4** BibTeX bibliography listing relevant references included in the *SylvanSeeds* database.
+**Supporting Information 5** *SylvanSeeds* database in a single *.csv* file.
 
@@
 The database is provided as Supporting Information.
-It can be visualized with the *SylvanSeeds* app at http://sylvanseeds.shinyapps.io/sylvanseeds/.
+It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.
 The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).

### 2020-08-12 doc/ms/v5_JVS/response-reviewers.Rmd
JVS R1

---
title: "Ref. JVS-R-05435 - Response to reviewers"
author: "Eduardo Fernández Pascual"
date: "12/8/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Editor's comments

> Thanks for your contribution. Two reviewers think your work is valuable but it is necessary you better define the biome (and geographic) scope for inclusion in the database, and also revisit the available data that contributes to your database. You'll see that one reviewer thinks you've missed lots of relevant information. Please address these concerns. If you can do this, the quality of the database will be greatly improved.

Please, find below the response to the comments of the reviewers.

# Referee 1's comments

> This manuscript suggests publication and description of an important data-base on germination features for temperate woodland plants, one of the largest and best documented to date. The data-base has been well prepared, described in detail and two figures summarize geographical extent, variation and mean values.
The amount of data is enormous, and will be an important tool to analyse features of regeneration by seed for forest ecosystems in the world.
The authors restrict their data-base to “Northern Hemisphere” but include on the map biomes and records from Chile, Australia and New Zealand, this should be either corrected in text or in the figure to make it coherent.

We restricted the collection of data to frequent species occurring in vegetation plots of the northern hemisphere. However, the web search for germination data found records of experiments performed with material of those species that had been collected in the southern hemisphere. In other words, the database is for the nemoral flora of the northern hemisphere, but the records come from both that area and other areas where the species can be found. We have added two sentences to the Summary of contents section of the results to clarify this point: *Although the frequent species list was created using only relevés from the northern hemisphere, the web search of germination articles found studies of those species that had been performed in the southern hemisphere. These records are included in the database, and their geographical origin is reported*.

> As to the extent of the biomes it should be stated somewhere that all of these forests undergo frosts (except most of Australia). The ecological description of the biome used might be further be extended with abiotic factors that separate this biome from adjacent ones (frost, drought, etc).

We have included this descriptive sentence in the introduction: *Generally, these forests are characterized by some frost events during the winter while summers are moist and do not suffer drought for any relevant length of time, conditions that favour the dominance of broadleaf deciduous trees*.

> Probably the WWF forest biome source used is not the most relevant here, a map based on the Köppen climate classification or similar would simplify the understanding of the map and also probably better match records to the biome map.

We agree that the Köppen climate classification would probably be more recognisable for many readers. However, we used the WWF classification for a practical reason: it includes a biogeographical regionalization (the ecoregions) which we used to stratify the random sampling of the vegetation plots from which we constructed the frequent species list (please see the methods section for a longer description of the procedure).  We did this to get a homogeneous sampling across the biogeographical regions of the biome. Since this is the regionalization that we used to create the species list, we believe that we should keep the WWF map to delimit the study area. However, to facilitate understanding with the Köppen system, we have included this sentence in the introduction: *Deciduous forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers, corresponding with the Cf climate in Köppen's classification (mild temperate, fully humid)*.

> L57: may be You can use “nemoral biome” explaining it as “Temperate Broadleaf and Mixed Forests biome of the northern hemisphere” and avoiding a long and difficult to follow abbreviation? (TBMFNH) or “temperate woodlands” ? This might help to read the text

We have adopted the *nemoral biome* abbreviation in the text, as suggested.

> L193 : may be replace Sown_by_container by Number_per_container

Done.

> L195 : you want to say the “last day” when seeds were counted?

Yes, corrected.

> L195: do you have data on the scarification (=permeabilizing seed coats) method? (physical abrasion, acid treatment, heat shock)?

Sorry, but we did not record this information.

> L201: do you have data on the duration of stratification?

Yes, when this information was reported in the original paper. It is recorded in the column *Stratification_days*.

> L211: why “germinable”? Some of them might have been dead at the beginning? May be “Number_seed” used?

Changed to *Number_seeds*.

> L173: do you maintain a version and backup system for this database in the case updates may come?

The database is maintained in a GitHub repository, which provides a version control system. The repository will be made open when the manuscript is accepted for publication. A website will also be provided, where it will be possible (i) to access the last version of the database; (ii) to be informed about updates; and (iii) to get in contact, to join and contribute data to the database. Please see the last sentences that have been added at the end of the discussion.

> L219: do You think this app can be extended to add data to the data-base?

The app functionality is limited to visualization of the dataset and, as far as we know at this moment, cannot be expanded into a GUI to submit and incorporate data to the database. However, the addition of new data is possible and easy to do using the R code that is behind the app. The website where the app and the database are hosted will provide information on how to contribute data to the database.

# Referee 2's comments

> The idea for a deciduous forest database for seed germination is excellent.  
Some things need to be made more clear than they are now.  The list of included species is relatively short, when one considers the size of the flora of the deciduous forest biome and the amount of work that has been done on seed germination of members of this biome.  Further, species from subalpine coniferous species have been included, and they need to be separated from the deciduous forest species.
Lines 57.  Whose vegetation classification system are you using?   What is the source for the name Temperate Broadleaf and Mixed Forests?

This is the official name of the WWF biome, which we used to sample the vegetation plots that provided the species list (please see the methods, and the response to referee 1). For clarity, we have also added the WWF reference at the first mention of the name in the introduction.

> Line 64. “Baskin, 1995”  is not a good reference to use here.  Why not the Baskin and Baskin 2014 book on seeds?   This reference is not correct on line 64 or in the Literature Cited.   It should be Baskin et al., 1995.  The authors of this paper are Baskin, C. C., Meyer, S.E. and Baskin, J.M.   Also, this paper is not about species that grow in the deciduous forests per se.

We have changed the reference to the Baskin book, as suggested.

> Lines 86-88.  You need to explain to the reader why you have included subalpine coniferous forests of the Cascade Mountains in the same category as deciduous (nemoral) forests of USA, China and Europe.  What vegetation classification systems puts these very different kinds of forests together?

The referee is right that the Cascadia ecoregions do not belong in the TBMF biome. The truth is that these regions were included in the search for practical reasons related to the way the project's workflow was organised, and are unrelated to the deciduous forest biome. Once we had germination records for species from these regions, we had to make the difficult decision of either keeping them (as they are indeed valuable data which might be of interest to the users of the database) or removing them (to keep the homogeneity of the deciduous forest concept).

We have tried to explain this better in the methods section. We have also included a column with the biome variable in the dataset, so the records belonging to species from Cascadia can be identified and separated at any time. Alternatively, if the editor considers it more reasonable, those records could be removed from the dataset and the manuscript.

> Pages 21-500   What is the meaning of all these pages?  These must be references you consulted, but there is no explanation.

These are the supporting materials, please see the Supporting Information section (which is after the bibliography) for a description of the files. We tried to uploaded these files in specific formats (a csv data file and BibTeX bibliographies) but the online submission system forced us to transform them to pdf and appended them at the end of the manuscript. We are sorry by this inconvenience.

> I was shocked when I saw your list of species.  It is not very complete for the deciduous forests, even for eastern North America.  There must be over 100 papers from the Baskin’s work that you have not included.  You should take a look at the Baskin and Baskin (2014) book on seeds.  Look at the list of papers of their own work that they cite.
  I think the idea behind this project is noble and the product will be of great use to people.  However, at this point I think the project is far from being complete.  Also, I think mixing species from the deciduous forests with those from subalpine coniferous forests will create confusion for people in the future who try to use this data base.

We agree that the database is not complete, but we argue that a project of this nature can never be truly complete. As we discuss with the other referee (please also see the new sentences at the end of the discussion) this is a database that intends to be alive, being updated and expanded with future projects, and welcoming collaborators who want to contribute new datasets.

We followed a systematic approach to search for data, with the purpose of prioritising work and maximising its utility for vegetation science. In short, this approach consisted in (i) obtaining a representative number of vegetation plots for the biome from sPlot (https://www.idiv.de/en/splot.html); and (ii) using the plots to produce a list of frequent species (i.e. species that occur in at least 5 % of the plots of a region). Please see the methods for more details.

This systematic approach may leave out relevant information on species of the biome (as the case mentioned by the referee) for three reasons: (1) the species is not recorded in the vegetation databases; (2) the species has been recorded, but it is infrequent; or (3) the species is recorded and frequent and goes into our list, but the relevant germination papers are not found by our web search because the species names is not mentioned in the title or the abstract. While points 1 and 2 are intentionally excluded by our methodology, point 3 would be a failure of the methodology (specifically, a failure of the search string to find a relevant paper).

For this reason, we had applied a protocol to detect the importance of point 3. Incidentally, this protocol used the Baskin book. The protocol consisted in the following: After completing the database, we took the species in our frequent species list for which we had not found relevant papers and searched them in the taxonomical index of the Baskin book. There were 273 species with missing data and mentioned by the Baskins in their index. We took a random sample of 10% of these species and searched the original references in the Baskin book, and found that all of them were either inaccessible (national journals or old conference proceedings not available online) or had no relevant data (i.e. provided no primary germination data that we could retrieve). From this trial, we concluded that our search string had found a reasonable amount of the available information, by comparing it to the best reference possible, the review of the Baskins.

Therefore, the articles mentioned by the referee mostly pertain to species that we intentionally left out of the systematic approach, because of their low representation in vegetation databases. Although of course the approach suggested by the referee is valid, and the information on those works valuable, it is also opportunistic (i.e. it would include references that we are personally aware of, instead of the systematic set of references found by the search based on occurrence in vegetation plots). It is difficult to see where this opportunistic approach would justifiably stop looking for more papers, and consider the database complete.

We believe that the amount of data we provide (primary data extracted from more than 600 references) justifies its utility and the publication of this report as a first building block of a database that will be expanded and maintained. The utility of the dataset is specially justified because, by focusing on frequent species from vegetation databases, it maximises its value for vegetation scientists. As it stands now, it is a good sample of frequent species of the deciduous forest of the northern hemisphere, with a good representation of, for example, many of the dominant tree species.

### 2020-08-12 doc/ms/v5_JVS/ms.Rmd
JVS R1

--- 2020-06-30 doc/ms/v4_JVS/ms.Rmd
@@
 Amongst these are temperature [@RN2249], diurnal temperature alternation [@RN2217], light [@RN4656] and seed dormancy inductors and relievers [@RN3063].
-All of these signals interact to produce a coarse- and fine-scale regulation of germination timing, integrating inputs from both seasonal climatic cycles [@RN3132] and local environmental gradients [@RN2865].
+All these signals interact to produce a coarse- and fine-scale regulation of germination timing, integrating inputs from both seasonal climatic cycles [@RN3132] and local environmental gradients [@RN2865].
 The practical consequence of this is that the response of seeds to, for example, light will depend on other conditions set by the experimenter.
@@
 
-To fill this gap, this article presents *SylvanSeeds*, a first global database of raw germination data for an ecologically and biogeographically coherent unit: the Temperate Broadleaf and Mixed Forests biome of the northern hemisphere (*TBMFNH*).
-Deciduous forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers.
+To fill this gap, this article presents *SylvanSeeds*, a first global database of raw germination data for an ecologically and biogeographically coherent unit: the temperate broadleaf and mixed forests biome [@RN4667] of the northern hemisphere (hereafter shortened to nemoral biome).
+Nemoral forests are dominant in temperate latitudes with mild to cold winters and relatively warm and wet summers, corresponding with the Cf climate in Köppen's classification (mild temperate, fully humid) [@RN4932].
+Generally, these forests are characterized by some frost events during the winter while summers are moist and do not suffer drought for any relevant length of time, conditions that favour the dominance of broadleaf deciduous trees [@RN4931].
 In the northern hemisphere, they also form a coherent evolutionary and biogeographic unit, sharing a common Tertiary history until they became separated between North America, Asia and Europe [@RN4684].
-At the same time, a relatively high number of classic seed biology research groups have worked within the *TBMFNH* areas, e.g.
-in the USA [@RN1045], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188].
-To create *SylvanSeeds*, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the *TBMFNH*.
+At the same time, a relatively high number of classic seed biology research groups have worked within the nemoral biome areas, e.g.
+in the USA [@RN3214], the UK [@RN3273], Belgium [@RN656] and Japan [@RN1188].
+To create *SylvanSeeds*, a systematic literature search [@RN2401] was applied to a list of frequent species representing the flora of the nemoral biome.
 This article makes the database accessible to the research community.
@@
 The terrestrial regionalization of the *World Wildlife Fund* [@RN4667] was used to select plots according to their coordinates.
-To ensure that plots were a representative sample of *TBMFNH* biodiversity, they were chosen from `r MSecoregions` ecoregions distributed throughout the northern hemisphere: 17 ecoregions of the Temperate Broadleaf and Mixed Forests biome (*Appalachian mixed mesophytic forests*, *Atlantic mixed forests*, *Cantabrian mixed forests*, *Caspian Hyrcanian mixed forests*, *Central Korean deciduous forests*, *Dinaric Mountains mixed forests*, *Euxine-Colchic broadleaf forests*, *Hokkaido deciduous forests*, *Manchurian mixed forests*, *Nihonkai evergreen forests*, *Nihonkai montane deciduous forests*, *Pindus Mountains mixed forests*, *Southeastern mixed forests*, *Taiheiyo evergreen forests*, *Taiheiyo montane deciduous forests*, *Western European broadleaf forests*, *Western Great Lakes forests*), plus three neighbouring ecoregions of the Temperate Coniferous Forest biome (*Cascade Mountains leeward forests*, *Central and Southern Cascades forests*, *Eastern Cascades forests*).
+To ensure that plots were a representative sample of nemoral biome biodiversity, they were chosen from 17 ecoregions of the Temperate Broadleaf and Mixed Forests biome distributed throughout the northern hemisphere: (*Appalachian mixed mesophytic forests*, *Atlantic mixed forests*, *Cantabrian mixed forests*, *Caspian Hyrcanian mixed forests*, *Central Korean deciduous forests*, *Dinaric Mountains mixed forests*, *Euxine-Colchic broadleaf forests*, *Hokkaido deciduous forests*, *Manchurian mixed forests*, *Nihonkai evergreen forests*, *Nihonkai montane deciduous forests*, *Pindus Mountains mixed forests*, *Southeastern mixed forests*, *Taiheiyo evergreen forests*, *Taiheiyo montane deciduous forests*, *Western European broadleaf forests*, *Western Great Lakes forests*).
 Although temperate broadleaf and mixed forests also occur in a smaller area of the southern hemisphere, these southern forests form a separate evolutionary and biogeographical unit, not being related by a common history like the northern hemisphere ones [@RN4684].
 For this reason, they were not considered.
+For reasons unrelated to the deciduous forest search, three neighbouring ecoregions of the Temperate Coniferous Forest biome (*Cascade Mountains leeward forests*, *Central and Southern Cascades forests*, *Eastern Cascades forests*) were included in the search, and their species were searched for in parallel.
+For completeness, data from these three regions is also included with the database, but the records from the coniferous forest species are identified so they can be excluded at will (see below).
+
 All chosen relevés had been classified as forest plots by *sPlot*, i.e.
@@
 To obtain the final list of species, only species that were present in at least 5% of the relevés of an ecoregion were kept, rendering a list of `r MSfrequentspp` frequent species.
-There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of *TBMFNH*, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.).
-The result is a list of plant species that occur with relatively high frequency in forest plots of the *TBMFNH*; this includes trees, shrubs and shade-tolerant forbs and grasses, as well as common semi-open species from forest margins, secondary forests, ruderalized forest plots, etc.
+There were two reasons to use this frequency threshold: (i) it made the search achievable with the resources available; and (ii) it filtered out rare species that may not be representative of the nemoral biome, and which could have been recorded for a variety of reasons (wrong taxonomical identifications, mistakes in plot coordinates, border areas, unnatural areas such as parks, etc.).
+The result is a list of plant species that occur with relatively high frequency in forest plots of the nemoral biome; this includes trees, shrubs and shade-tolerant forbs and grasses, as well as common semi-open species from forest margins, secondary forests, ruderalized forest plots, etc.
 
@@
 \@ref(fig:fig1)**), in both hemispheres.
+Although the frequent species list was created using only relevés from the northern hemisphere, the web search of germination articles found studies of those species that had been performed in the southern hemisphere.
+These records are included in the database, and their geographical origin is reported.
 The oldest record was from 1920 and the top three contributing countries were the USA (`r MScountries[1, 2]`), the UK (`r MScountries[2, 2]`) and Japan (`r MScountries[3, 2]`).
@@
 The database is provided as a *csv* file, comma separated, named **Supporting Information 5** (see online Supporting Information).
-The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Sown_by_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Germinable* (count of seeds used in the experiment).
+The first row of the file contains the header data, with the following variables: *Biome* (whether the species belongs to temperate broadleaf and mixed foresta [TBMF] or to the temperate coniferous biome [TCF]), *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment).
 Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions.
 Presenting the response variable as a proportion (i.e.
-number of successes *Germinated*, number of trials *Germinable*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].
+number of successes *Germinated*, number of trials *Number_seeds*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].
 
@@
 Second, the database and the app can serve as a standard in further efforts to compile and standardize seed germination data.
+The version of the database presented here is a first building block that will be expanded by updating it with more records and integrating it with datasets from other biomes and regions.
+The website https://efernandezpascual.shinyapps.io/sylvanseeds/ will publish and describe updates.
+All people interested in contributing to the growth of this germination database are encouraged to contact the corresponding author.
 
@@
 All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
-The database is provided as Supporting Information.
+The database is provided as Supporting Information of this manuscript, but please do visit https://efernandezpascual.shinyapps.io/sylvanseeds/ to check for updates.
 It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.

### 2020-08-12 src/cleaning.r

@@ -86,6 +86,21 @@ Names %>%
   select(New.ID, Species, SpeciesNew) %>% 
   arrange(Species) -> dfFrequentNames
 
+merge(dfCounts, dfTotals, by = "Ecoregion") %>%
+  mutate(F = N/T) %>%
+  filter(! Ecoregion %in% c("Cascade Mountains leeward forests", "Central and Southern Cascades forests", 
+                            "Eastern Cascades forests")) %>%
+  filter(F > 0.05) %>% 
+  select(New.ID) %>%
+  unique %>%
+  merge(Names) %>% 
+  mutate(Species = paste(Genus, Species, sep = " "),
+         SpeciesNew = paste(New.Genus, New.Species, sep = " ")) %>% 
+  select(SpeciesNew) %>% 
+  unique %>%
+  arrange(SpeciesNew) %>%
+  pull(SpeciesNew) -> TBMFspp
+
 ## Create Boolean search string
 
 rbind(
@@ -127,9 +142,9 @@ WoS %>%
   mutate(PopulationID = as.factor(PopulationID),
          ReferenceID = as.factor(ReferenceID),
          TPLName = as.factor(paste(New.Genus, New.Species)),
-         Germinable = Replicates * Sown.per.replicate,
-         Germinated = round((Germination * Germinable)/100, 0),
-         Germinated = ifelse(Germinated > Germinable, Germinable, Germinated),
+         Number_seeds = Replicates * Sown.per.replicate,
+         Germinated = round((Germination * Number_seeds)/100, 0),
+         Germinated = ifelse(Germinated > Number_seeds, Number_seeds, Germinated),
          Stratification = as.factor(ifelse(Stratification_type == "None", "N", "Y")),
          GA3 = as.factor(ifelse(GA == 0, "N", "Y")),
          Light = as.factor(ifelse(Photoperiod == 0, "N", "Y")),
@@ -140,13 +155,15 @@ WoS %>%
                            labels = c("-5", "0", "5", "10", "15",
                                       "20", "25", "30", "35", "40", "45")),
          Container_number = Replicates,
-         Sown_by_container = Sown.per.replicate,
+         Number_per_container = Sown.per.replicate,
          Incubation_days = Length.experiment,
          Dry_storage = Dry.storage) %>%
+  mutate(Biome = ifelse(TPLName %in% TBMFspp, "TBMF", "TCF")) %>%
[…]

### 2020-09-15 README.Rmd
JVS minor revision

--- 2020-06-06 README.Rmd
@@
 
-# Sylvan Seeds
+![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.jpg)
 
-*Sylvan Seeds* is a database of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere.
-It contains data on >300 plant species, obtained from >600 published references.
+# SylvanSeeds, a seed germination database for temperate deciduous forests
+
+This repository stores all the information related to the publication *SylvanSeeds, a seed germination database for temperate deciduous forests*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.
+
+*SylvanSeeds* is a dataset of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere.
+It contains data on >300 plant species, obtained from >500 published references.
 The data is in the form of germination proportions recorded under experimental combinations of temperature, light, scarification and stratification.
@@
 
+This repository is organised following the advice of [Wilson et al. 2017](https://doi.org/10.1371/journal.pcbi.1005510) for recording and storing research projects.
+
 The following materials are available in this repository:
 
-* [The database file itself is `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
-* [The Sylvan Seeds `shiny` app for visualizing the database](https://sylvanseeds.shinyapps.io/sylvanseeds/)
-* The article describing the collection and fields of the database, which is in preparation.
+* `data` Original raw files including the primary result of the search in the Web of Science, and search notes.
+* `doc` Files to create the manuscript using `Rmarkdown`.
+* `results` Output of the `R` scripts, including the clean database and files needed to create the manuscript.
+* `src` Scripts in `R` language used to clean the raw data, perform the analyses of the manuscript, and build the `SylvanSeeds` app.
+* [The database itself in `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
+* [The SylvanSeeds `shiny` app for visualizing the dataset](https://sylvanseeds.shinyapps.io/sylvanseeds/)
+* [The report paper describing the collection and fields of the dataset](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md), published in the Journal of Vegetation Science.
+
+## Citation
+
+Please cite the dataset as
+
+> Fernández-Pascual, E (2020) SylvanSeeds, a seed germination database for temperate deciduous forests. Journal of Vegetation Science, in press.

### 2020-09-15 doc/manuscript.Rmd
JVS minor revision

--- 2020-08-12 doc/ms/v5_JVS/ms.Rmd
@@
 The list was searched in the Web of Science.
-6,791 references were screened, finding 614 articles from which data were extracted.
+6,791 references were screened, finding 555 articles from which data were extracted.
 *SylvanSeeds* includes `r MSrecords` germination records of `r MSspecies` species from `r MSfamilies` families (gymnosperms and angiosperms), collected in 46 countries between 1920-2017.
@@
 
-**Keywords:** germination database, germination temperature, light and dark germination, seed dormancy, seed traits, temperate coniferous forests, temperate broadleaf and mixed forests, temperate evergreen forests
+**Keywords:** germination database, germination temperature, light and dark germination, nemoral, seed dormancy, seed traits, temperate broadleaf and mixed forests, temperate evergreen forests
 
@@
 
-## Species list
+## Frequent species list
+
+A systematic approach was followed to search for data, with the purpose of prioritising work and maximising its utility for vegetation science.
+In short, this approach consisted in (i) obtaining a representative number of vegetation plots for the biome from sPlot (https://www.idiv.de/en/splot.html); and (ii) using the plots to produce a list of frequent species (i.e.
+species that occur in at least 5 % of the plots of a region).
 
@@
 For this reason, they were not considered.
-For reasons unrelated to the deciduous forest search, three neighbouring ecoregions of the Temperate Coniferous Forest biome (*Cascade Mountains leeward forests*, *Central and Southern Cascades forests*, *Eastern Cascades forests*) were included in the search, and their species were searched for in parallel.
-For completeness, data from these three regions is also included with the database, but the records from the coniferous forest species are identified so they can be excluded at will (see below).
 
@@
 their plant cover was dominated by tree species.
-The taxa names were standardized to species level with *The Plant List* [-@RN2321] using the *Taxonstand* package [@RN4660] in *R* version 3.6.2 [@RN2315].
+The taxa names were standardized to species level with *The Plant List* [-@RN2321] using the *Taxonstand* package [@RN4660] in *R* [@RN2315].
 The final vegetation database contained `r MSplots` relevés and `r MStotalspp` standardized species names, considering only seed plants (gymnosperms and angiosperms), and encompassing all forest layers.
@@
 This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results.
-The processing of these results is described in a PRISMA flow diagram (**Supporting Information 1**).
+The processing of these results is described in a PRISMA flow diagram (**Appendix S1**).
 A first filter of the results by the relevance of the title retained 1,489 references.
@@
 Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal issues which had not been digitalised.
-The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Supporting Information 2**) in case they can be processed in the future.
+The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Appendix S2**) in case they can be processed in the future.
 The found texts were accessed to retrieve data for the database.
@@
 use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins).
-Of the accessed references, 639 were non-relevant (*BiBTeX* file in **Supporting Information 3**) and 614 provided relevant data (*BiBTeX* file in **Supporting Information 4**).
+Of the accessed references, 698 were non-relevant (*BiBTeX* file in **Appendix S3**) and 555 provided relevant data (*BiBTeX* file in **Appendix S4**).
+
+The systematic approach applied may fail to capture references on species belonging to the nemoral biome for three reasons: (1) the species is not recorded in the vegetation database; (2) the species has been recorded, but it is infrequent (see above the frequency criterion); or (3) the species is recorded and frequent and goes into the list, but the relevant germination references are not found by the web search because the species name is not mentioned in the title or the abstract.
+While points 1 and 2 are intentionally excluded by the applied methodology, point 3 would be a failure of the methodology (specifically, a failure of the search string to find a relevant paper).
+For this reason, a protocol was applied to detect the importance of point 3, using the book of Baskin and Baskin [-@RN3214] as a reference.
+After completing the database, species names in the frequent species list for which no relevant papers had been found were searched in the taxonomical index of the Baskin and Baskin book.
+There were 273 species with missing data and mentioned by Baskin and Baskin in their index.
+A random sample of 10 % of these species were selected, and their references as mentioned in the book were searched.
+All of them were found to be either inaccessible (national journals or old conference proceedings not available online) or to have no relevant data (i.e.
+provided no primary germination data that could be retrieved).
+From this trial, it was concluded that the search string had found a reasonable amount of the available information, by comparing it to the best reference available, the review book of Baskin and Baskin.
 
@@
 
-The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 614 references.
+The final database contains `r MSrecords` records (germination proportions for a given seed lot of a species, recorded in a set of experimental conditions) from 555 references.
 The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig.
@@
 
-The database is provided as a *csv* file, comma separated, named **Supporting Information 5** (see online Supporting Information).
-The first row of the file contains the header data, with the following variables: *Biome* (whether the species belongs to temperate broadleaf and mixed foresta [TBMF] or to the temperate coniferous biome [TCF]), *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment).
+The database is provided as a *csv* file, comma separated, named **Appendix S5** (see online Supporting Information).
+The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment).
 Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions.
@@
 
-**Supporting Information 1** PRISMA 2009 flow chart describing the process of reference screening and inclusion.
-**Supporting Information 2** BibTeX bibliography listing the not found full texts.
-**Supporting Information 3** BibTeX bibliography listing the non-relevant references.
-**Supporting Information 4** BibTeX bibliography listing relevant references included in the *SylvanSeeds* database.
-**Supporting Information 5** *SylvanSeeds* database in a single *.csv* file.
+**Appendix S1** PRISMA 2009 flow chart describing the process of reference screening and inclusion.
+**Appendix S2** Bibliography in BibTeX format listing the not-found full texts.
+**Appendix S3** Bibliography in BibTeX format listing the non-relevant references.
+**Appendix S4** Bibliography in BibTeX format listing the relevant references included in the *SylvanSeeds* database.
+**Appendix S5** *SylvanSeeds* database in a single *.csv* file.
 
@@
 All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
-The database is provided as Supporting Information of this manuscript, but please do visit https://efernandezpascual.shinyapps.io/sylvanseeds/ to check for updates.
+The database is provided as Appendix S5 of this manuscript, but please do visit https://efernandezpascual.shinyapps.io/sylvanseeds/ to check for updates.
 It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.

### 2020-09-15 app.R

@@ -9,7 +9,7 @@ spp <- WoSDB %>% select(TPLName) %>% arrange(TPLName) %>% pull(TPLName) %>% uniq
 ui <- fluidPage(
 
     # Application title
-    titlePanel("Sylvan Seeds: Germination database of temperate broadleaf and mixed forests"),
+    titlePanel("SylvanSeeds: Germination database of temperate broadleaf and mixed forests"),
 
     # Sidebar to choose species to display
     sidebarLayout(

### 2020-09-15 src/NewPhytol figures.R

@@ -1,9 +1,0 @@
-library(tidyverse); library(here)
-
-load(file = here("results", "msfigs.RData"))
-
-ggsave(p1, file = here("doc", "ms", "v3_NewPhytol", "Fig1.png"), 
-       path = NULL, scale = 1, width = 150, height = 80, units = "mm", dpi = 600)
-
-ggsave(p2, file = here("doc", "ms", "v3_NewPhytol", "Fig2.png"), 
-         path = NULL, scale = 1, width = 150, height = 160, units = "mm", dpi = 600)

### 2020-09-15 src/cleaning.r

@@ -1,20 +1,20 @@
 library(tidyverse); library(here); library(sp); library(openxlsx)
 
-# Cleaning of the search string (Supplementary file 1)
+# Cleaning of the search string
 
 ## TPL Names from common source
 
-read.csv("../#tpl/results/TPLNames.csv") -> Names
-read.csv("../#tpl/results/Families.csv") -> SeedFamilies
+read.csv("../#tpl/results/TPLNames.csv") -> Names # TPL taxonomy files are in my home drive
+read.csv("../#tpl/results/Families.csv") -> SeedFamilies # TPL taxonomy files are in my home drive
 
-## Species file
+## Clean species file
 
 rbind(
-  read.csv("../#plots/data/sPlot12/species_Edu.csv") %>% 
+  read.csv("../#plots/data/sPlot12/species_Edu.csv") %>% # sPlot vegetation files are in my home drive
     select(PlotObservationID, species, Relative.cover) %>%
     rename(Cover = Relative.cover, PlotID = PlotObservationID, Taxon = species) %>%
     mutate(PlotID = paste("Rest", PlotID, sep = "_")),
-  read.csv("../#plots/data/sPlot12/forest2_1500.csv", sep = "\t") %>%
+  read.csv("../#plots/data/sPlot12/forest2_1500.csv", sep = "\t") %>% # sPlot vegetation files are in my home drive
     select(Relevé.number, Species.name, Cover..) %>%
     rename(Cover = Cover.., PlotID = Relevé.number, Taxon = Species.name) %>%
     mutate(PlotID = paste("Japan", PlotID, sep = "_"))) %>%
@@ -22,10 +22,10 @@ rbind(
   filter(Family %in% SeedFamilies$Family) %>%
   select(PlotID, New.ID, Cover) -> dfSpeciesRevised
 
-## Header file
+## Clean plot header file
 
 rbind(
-  read.csv("../#plots/data/sPlot12/TDFNH3_Edu.csv") %>%
+  read.csv("../#plots/data/sPlot12/TDFNH3_Edu.csv") %>% # sPlot vegetation files are in my home drive
     filter(Herbs.identified..y.n. != "N" | 
              ! Plants.recorded %in% c("All trees & dominant shrubs", 
                                       "All woody species", 
@@ -42,9 +42,9 @@ rbind(
[…]

### 2020-09-15 src/visualizeDB.R

@@ -1,6 +1,6 @@
 filtrar <- function(df, sp = "Quercus robur") filter(df, Species == sp)
 
-references <- function(df1 = WoSDB, sp = "Quercus robur") {
+references <- function(df1 = TBMFDB, sp = "Quercus robur") {
   filter(df1, TPLName == sp) %>%
     select(Reference) %>%
     unique %>%

### 2020-09-15 README.Rmd
manuscript as github document

@@
 * `src` Scripts in `R` language used to clean the raw data, perform the analyses of the manuscript, and build the `SylvanSeeds` app.
-* [The database itself in `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
-* [The SylvanSeeds `shiny` app for visualizing the dataset](https://sylvanseeds.shinyapps.io/sylvanseeds/)
-* [The report paper describing the collection and fields of the dataset](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md), published in the Journal of Vegetation Science.
 

### 2020-09-15 doc/manuscript.Rmd
manuscript as github document

@@
 subtitle: "Running title: SylvanSeeds, a forest germination database"
-output: 
-  bookdown::word_document2:
-    reference_docx: template.docx
+output: github_document
+  # bookdown::word_document2:
+  #   reference_docx: template.docx
 bibliography: refs.bib

### 2020-09-15 src/cleaning.r

@@ -210,7 +210,7 @@ WoSDB %>%
   select(-Biome) -> TCFDB # Temperate coniferous forest database
 
 readr::write_excel_csv(TBMFDB, here::here("results", "TBMF_Database.csv"))
-readr::write_excel_csv(TCFDB, here::here("results", "TCFDB_Database.csv"))
+readr::write_excel_csv(TCFDB, here::here("results", "TCF_Database.csv"))
 
 # Calculate numbers for the manuscript main text
 

### 2020-09-15 README.Rmd
3rd submission to JVS 🌳🍋

@@
 
-![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.jpg)
+![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.JPG)
 
@@
 
-This repository stores all the information related to the publication *SylvanSeeds, a seed germination database for temperate deciduous forests*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.
-
-*SylvanSeeds* is a dataset of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere.
+[*SylvanSeeds*](https://efernandezpascual.github.io/home/sylvanseeds.html) is a database of seed germination ecology for the temperate broadleaf and mixed forest biome of the northern hemisphere.
 It contains data on >300 plant species, obtained from >500 published references.
 The data is in the form of germination proportions recorded under experimental combinations of temperature, light, scarification and stratification.
+
+This repository stores all the information related to the publication *SylvanSeeds, a seed germination database for temperate deciduous forests*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.
+It also stores the code of the *SylvanSeeds* `shiny` app, that can be used to visualize the database.
 
@@
 
-Please cite the dataset as
+Please cite `SylvanSeeds` as:
 

### 2020-09-15 doc/manuscript.Rmd
3rd submission to JVS 🌳🍋

--- 2020-09-15 doc/manuscript.Rmd
@@
 Seed traits have functional significance in all levels of plant biology, but there is a lack of germination databases of wide geographical scope.
-This article presents *SylvanSeeds*, a first global database of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests.
+This report presents *SylvanSeeds* (https://efernandezpascual.github.io/home/sylvanseeds.html), a first global database of germination records for an ecologically coherent unit: Temperate Broadleaf and Mixed Forests.
 Data were gathered with a systematic literature search.
@@
 *SylvanSeeds* is freely distributed as a *.csv*.
-The shiny app *SylvanSeeds* (https://efernandezpascual.shinyapps.io/sylvanseeds/) is also presented, to make data accessible to the public.
+A shiny web app is also presented, to make data accessible to the public.
 *SylvanSeeds* advances functional seed ecology and brings two innovations to plant science.
@@
 The version of the database presented here is a first building block that will be expanded by updating it with more records and integrating it with datasets from other biomes and regions.
-The website https://efernandezpascual.shinyapps.io/sylvanseeds/ will publish and describe updates.
+The website https://efernandezpascual.github.io/home/sylvanseeds.html will publish and describe updates.
 All people interested in contributing to the growth of this germination database are encouraged to contact the corresponding author.
@@
 All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
-The database is provided as Appendix S5 of this manuscript, but please do visit https://efernandezpascual.shinyapps.io/sylvanseeds/ to check for updates.
+The database is provided as **Appendix S5** of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates.
 It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.
-The code of the app is stored at (note: the GitHub repo is kept private until publication of the manuscript).
+The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds.
 
@@
 Each golden circle is a record.
-The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.", fig.align = "center", fig.width=7, fig.height=3}
+The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.", fig.width=7, fig.height=3}
 p1
@@
 ```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "Example of the germination records as shown by the *SylvanSeeds* app.
-Records for one species, the European pedunculate oak, *Quercus robur*.
+Records for one species, the European common beech, *Fagus sylvatica*.
 Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel.
-Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.", fig.align = "center", fig.width=7, fig.height=9}
+Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.", fig.width=7, fig.height=5}
 p2

### 2020-09-15 app.R

@@ -3,9 +3,9 @@ library(shiny)
 library(tidyverse); library(maps); library(here)
 source(here("src", "visualizeDB.R"))
 load(here("results", "appdata.RData"))
-spp <- WoSDB %>% select(TPLName) %>% arrange(TPLName) %>% pull(TPLName) %>% unique %>% as.character
+spp <- TBMFDB %>% select(TPLName) %>% arrange(TPLName) %>% pull(TPLName) %>% unique %>% as.character
 
-# Define UI for application that draws a histogram
+# Define UI 
 ui <- fluidPage(
 
     # Application title
@@ -29,7 +29,7 @@ ui <- fluidPage(
     )
 )
 
-# Define server logic required to draw a histogram
+# Define server
 server <- function(input, output) {
 
     output$plot_map <- renderPlot({
@@ -48,7 +48,7 @@ server <- function(input, output) {
         seedplot(df = y)
     })
     output$table <- renderTable({
-        references(WoSDB, input$var)
+        references(TBMFDB, input$var)
     })
 }
 

### 2020-09-15 src/cleaning.r

@@ -382,54 +382,40 @@ save(Germination,TBMFDB, Places, TBMF,
 
 # Manuscript figures
 
-filtrar <- function(df, sp = "Quercus robur") filter(df, Species == sp)
+TBMFDB %>%
+  ggplot(aes(x = Longitude, y = Latitude)) + 
+  geom_polygon(data = map_data("world"), aes(x = long, y = lat, group = group), 
+               color = "gainsboro", fill = "gainsboro") +
+  geom_polygon(data = TBMF, aes(x = long, y = lat,group =  group), 
+               fill = "darkolivegreen4", color = "darkolivegreen4") +	
+  geom_point(color = "gold", size = 1.25, alpha = 0.5) +
+  ggthemes::theme_map() +
+  theme(legend.position = "none",
+        axis.title = element_blank()) +
+  coord_cartesian(xlim = c(-160, 180), ylim = c(-55, 80)) -> p1
 
-references <- function(df1 = TBMFDB, df2 = References, sp = "Quercus robur") {
-  filter(df1, Species == sp) %>%
-    select(ReferenceID) %>%
-    merge(df2) %>%
-    unique %>%
-    select(Reference) %>%
-    arrange(Reference) %>%
-    rename(References = Reference) %>%
-    as_tibble
-}
+Germination %>% 
+  filter(Species == "Fagus sylvatica") %>% 
+  ggplot(aes(x = as.factor(Temperature), y = mean, ymin = lower, ymax = upper, fill = Experiment)) + 
+  geom_bar(stat = "identity", alpha = 0.6, show.legend = FALSE) + 
+  geom_errorbar(aes(color = Experiment), width = 0.1, size = 1, 
+                position = position_dodge(.9), show.legend = FALSE) +
+  facet_wrap( ~ Experiment, scales = "free", ncol = 3) +
+  coord_cartesian(ylim = c(0, 1)) +
+  ylab(label = "Germination proportion") + xlab(label = "Average germination temperature (ºC)") +
+  ggthemes::theme_tufte() + 
+  theme(panel.background = element_rect(color = "grey96", fill = "grey96"), 
+        legend.position = "none", 
+        strip.text = element_text(size = 11),
+        axis.text = element_text(size = 12, face = "bold"),
+        axis.title = element_text(size = 14, face = "bold"),
+        legend.text = element_text(size = 16, face = "bold")) -> p2
 
-mapplot <- function(df, shape = TBMF) {
-  ggplot(df, aes(x = Longitude, y = Latitude)) + 
[…]

### 2020-09-15 src/visualizeDB.R

@@ -9,6 +9,7 @@ references <- function(df1 = TBMFDB, sp = "Quercus robur") {
     as_tibble
 }
 
+
 mapplot <- function(df, shape = TBMF) {
   ggplot(df, aes(x = Longitude, y = Latitude)) + 
     geom_polygon(data = map_data("world"), aes(x = long, y = lat, group = group), 

### 2020-10-12 README.Rmd
readme pic
small readme change
accepted ms 🌳🍋🌱

@@
 
-![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.JPG)
+![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.jpg)
 
@@
 
-This repository stores all the information related to the publication *SylvanSeeds, a seed germination database for temperate deciduous forests*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.
+This repository stores all the information related to the publication [*SylvanSeeds, a seed germination database for temperate deciduous forests*](https://doi.org/10.1111/jvs.12960), including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the [manuscript](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md).
 It also stores the code of the *SylvanSeeds* `shiny` app, that can be used to visualize the database.
@@
 * `data` Original raw files including the primary result of the search in the Web of Science, and search notes.
-* `doc` Files to create the manuscript using `Rmarkdown`.
+* `doc` Files to create the [manuscript](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md) using `Rmarkdown`.
 * `results` Output of the `R` scripts, including the clean database and files needed to create the manuscript.
@@
 
-> Fernández-Pascual, E (2020) SylvanSeeds, a seed germination database for temperate deciduous forests. Journal of Vegetation Science, in press.
+> Fernández-Pascual, E. (2020). [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science*

### 2020-10-12 doc/manuscript.Rmd
accepted ms 🌳🍋🌱

@@
 title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
-subtitle: "Running title: SylvanSeeds, a forest germination database"
-output: 
-  bookdown::word_document2:
-    reference_docx: template.docx
+output: github_document
 bibliography: refs.bib
@@
 In short, this approach consisted in (i) obtaining a representative number of vegetation plots for the biome from sPlot (https://www.idiv.de/en/splot.html); and (ii) using the plots to produce a list of frequent species (i.e.
-species that occur in at least 5 % of the plots of a region).
+species that occur in at least 5% of the plots of a region).
 
@@
 This string was searched in the *Thompson Reuters Web of Science* on 5 Mar 2019, returning 6,791 results.
-The processing of these results is described in a PRISMA flow diagram (**Appendix S1**).
+The processing of these results is described in a PRISMA flow diagram [(**Appendix S1**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf).
 A first filter of the results by the relevance of the title retained 1,489 references.
@@
 Most of these belonged to smaller publishers not included in the subscriptions of the University of Oviedo, and to older journal issues which had not been digitalised.
-The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file (**Appendix S2**) in case they can be processed in the future.
+The resources of this project did not make it possible to further pursue these references, but they are included as a *BibTeX* file [(**Appendix S2**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf) in case they can be processed in the future.
 The found texts were accessed to retrieve data for the database.
@@
 use of germination promoters such as the plant hormone gibberellic acid; drought treatments, including polyethylene glycol solutions; application of heavy metals or other pollutants; smoke-related germination promoters such as karrikins).
-Of the accessed references, 698 were non-relevant (*BiBTeX* file in **Appendix S3**) and 555 provided relevant data (*BiBTeX* file in **Appendix S4**).
+Of the accessed references, 698 were non-relevant (*BiBTeX* file in [**Appendix S3**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf)) and 555 provided relevant data (*BiBTeX* file in [**Appendix S4**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf)).
 
@@
 There were 273 species with missing data and mentioned by Baskin and Baskin in their index.
-A random sample of 10 % of these species were selected, and their references as mentioned in the book were searched.
+A random sample of 10% of these species were selected, and their references as mentioned in the book were searched.
 All of them were found to be either inaccessible (national journals or old conference proceedings not available online) or to have no relevant data (i.e.
@@
 The plant materials had been collected across the Temperate Broadleaf and Mixed Forest biome and surrounding areas (**Fig.
-\@ref(fig:fig1)**), in both hemispheres.
+1**), in both hemispheres.
 Although the frequent species list was created using only relevés from the northern hemisphere, the web search of germination articles found studies of those species that had been performed in the southern hemisphere.
@@
 
+```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.pos = "H", fig.cap = "**Figure 1** *Geographical distribution of the germination records in the database.
+Each golden circle is a record.
+The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.*", fig.width=7, fig.height=3}
+knitr::include_graphics("../results/Fig1.png")
+```
+
 ## Database file
 
-The database is provided as a *csv* file, comma separated, named **Appendix S5** (see online Supporting Information).
+The database is provided as a *csv* file, comma separated [(**Appendix S5**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv).
 The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment).
@@
 By visiting the app, users can consult the available germination information for a species (**Fig.
-\@ref(fig:fig2)**), the origin of its seed lots, and the bibliographical references for the species.
+2**), the origin of its seed lots, and the bibliographical references for the species.
+
+```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 2** *Example of the germination records as shown by the SylvanSeeds app.
+Records for one species, the European common beech, Fagus sylvatica.
+Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel.
+Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.*", fig.width=7, fig.height=5}
+knitr::include_graphics("../results/Fig2.png")
+```
 
@@
 
+# Supporting Information
+
+[**Appendices S1-S4**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf) PRISMA 2009 flow chart describing the process of reference screening and inclusion; bibliography in BibTeX format listing the not-found full texts, the non-relevant references and the relevant references included in the *SylvanSeeds* database.
+[**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv) *SylvanSeeds* database in a single *.csv* file.
+
+# Data accessibility
+
+All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
+The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates.
+It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.
+The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds.
+
 # References
@@
 :::
-
-# Supporting Information
-
-**Appendix S1** PRISMA 2009 flow chart describing the process of reference screening and inclusion.
-**Appendix S2** Bibliography in BibTeX format listing the not-found full texts.
-**Appendix S3** Bibliography in BibTeX format listing the non-relevant references.
-**Appendix S4** Bibliography in BibTeX format listing the relevant references included in the *SylvanSeeds* database.
-**Appendix S5** *SylvanSeeds* database in a single *.csv* file.
-
-# Data accessibility
-
-All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
-The database is provided as **Appendix S5** of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates.
-It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.
-The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds.
-
-# Figures
-
-```{r fig1, echo = FALSE, fig.pos = "H", fig.cap = "Geographical distribution of the germination records in the database.
-Each golden circle is a record.
-The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.", fig.width=7, fig.height=3}
-p1
-```
-
-```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "Example of the germination records as shown by the *SylvanSeeds* app.
-Records for one species, the European common beech, *Fagus sylvatica*.
-Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel.
-Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.", fig.width=7, fig.height=5}
-p2
-```

### 2020-10-12 src/cleaning.r

@@ -411,11 +411,11 @@ Germination %>%
         axis.title = element_text(size = 14, face = "bold"),
         legend.text = element_text(size = 16, face = "bold")) -> p2
 
-# ggsave(p1, file = "results/Fig1.tiff", 
-#        path = NULL, scale = 1, width = 170, height = 70, units = "mm", dpi = 600)
-# 
-# ggsave(p2, file = "results/Fig2.tiff", 
-#        path = NULL, scale = 1, width = 170, height = 150, units = "mm", dpi = 600)
+ggsave(p1, file = "results/Fig1.png",
+       path = NULL, scale = 1, width = 170, height = 70, units = "mm", dpi = 600)
+
+ggsave(p2, file = "results/Fig2.png",
+       path = NULL, scale = 1, width = 170, height = 150, units = "mm", dpi = 600)
 
 save(p1, p2,
      file = here::here("results", "msfigs.RData"))

### 2020-10-12 doc/manuscript.Rmd
release

@@
 title: "SylvanSeeds, a seed germination database for temperate deciduous forests"
-output: github_document
+output: pdf_document
 bibliography: refs.bib
@@
 **Author:** Eduardo Fernández-Pascual **Institutional address:** Departamento de Biología de Organismos y Sistemas, Universidad de Oviedo, C/ Catedrático Rodrigo Uría, 33006 Oviedo/Uviéu, Spain **Email:** efernandezpascual@gmail.com **Telephone:** +34985104787
+
+*This is the peer reviewed version of the following article: Fernández-Pascual, E.
+(2020).
+SylvanSeeds, a seed germination database for temperate deciduous forests.
+Journal of Vegetation Science, which has been published in final form at https://doi.org/10.1111/jvs.12960.*
 
@@
 
-```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.pos = "H", fig.cap = "**Figure 1** *Geographical distribution of the germination records in the database.
+```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Geographical distribution of the germination records in the database.
 Each golden circle is a record.
-The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.*", fig.width=7, fig.height=3}
-knitr::include_graphics("../results/Fig1.png")
+The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the WWF.", fig.width=7, fig.height=3}
+p1
 ```
@@
 
-```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 2** *Example of the germination records as shown by the SylvanSeeds app.
+```{r fig2, echo = FALSE, fig.cap = "Example of the germination records as shown by the SylvanSeeds app.
 Records for one species, the European common beech, Fagus sylvatica.
 Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel.
-Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.*", fig.width=7, fig.height=5}
-knitr::include_graphics("../results/Fig2.png")
+Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.", fig.width=7, fig.height=5}
+p2
 ```

### 2020-10-12 README.Rmd
corrected references
zenodo doi

@@
 ```
+
+[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4081377.svg)](https://doi.org/10.5281/zenodo.4081377)
 
@@
 
-> Fernández-Pascual, E. (2020). [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science*
+> Fernández-Pascual, E. (2020). [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science.*

### 2020-10-12 doc/manuscript.Rmd
zenodo doi

--- 2020-10-12 doc/manuscript.Rmd
@@
 
-```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.pos = "H", fig.cap = "**Figure 1** *Geographical distribution of the germination records in the database.
+```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "**Figure 1** *Geographical distribution of the germination records in the database.
 Each golden circle is a record.
-The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.*", fig.width=7, fig.height=3}
+The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the WWF.*", fig.width=7, fig.height=3}
 knitr::include_graphics("../results/Fig1.png")
@@
 
-```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 2** *Example of the germination records as shown by the SylvanSeeds app.
+```{r fig2, echo = FALSE, fig.cap = "**Figure 2** *Example of the germination records as shown by the SylvanSeeds app.
 Records for one species, the European common beech, Fagus sylvatica.
@@
 The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds.
+A version of record of the repository can be found at https://doi.org/10.5281/zenodo.4081377.
 

### 2020-10-27 README.Rmd
pub date
🍂
proof

@@
 
-> Fernández-Pascual, E. (2020). [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science.*
+> Fernández-Pascual E (2021) [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science.*

### 2020-10-27 doc/manuscript.Rmd
🍂
proof

@@
 load(here("results", "msnumbers.RData"))
-load(here("results", "msfigs.RData"))
 ```
@@
 
-The database is provided as a *csv* file, comma separated [(**Appendix S5**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv).
+The database is provided as a *csv* file, comma separated [(**Appendix S5**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv).
 The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment).
@@
 [**Appendices S1-S4**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf) PRISMA 2009 flow chart describing the process of reference screening and inclusion; bibliography in BibTeX format listing the not-found full texts, the non-relevant references and the relevant references included in the *SylvanSeeds* database.
-[**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv) *SylvanSeeds* database in a single *.csv* file.
+[**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv) *SylvanSeeds* database in a single *.csv* file.
 
@@
 All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
-The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates.
+The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates.
 It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.

### 2020-10-27 src/cleaning.r

@@ -411,11 +411,8 @@ Germination %>%
         axis.title = element_text(size = 14, face = "bold"),
         legend.text = element_text(size = 16, face = "bold")) -> p2
 
-ggsave(p1, file = "results/Fig1.png",
+ggsave(p1, file = "results/Fig1.pdf",
        path = NULL, scale = 1, width = 170, height = 70, units = "mm", dpi = 600)
 
-ggsave(p2, file = "results/Fig2.png",
-       path = NULL, scale = 1, width = 170, height = 150, units = "mm", dpi = 600)
-
-save(p1, p2,
-     file = here::here("results", "msfigs.RData"))
+ggsave(p2, file = "results/Fig2.pdf",
+       path = NULL, scale = 1, width = 170, height = 120, units = "mm", dpi = 600)

### 2020-11-12 README.Rmd
revised folder structure 🍂

@@
 
-![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.jpg)
+![SylvanSeeds](2017070313 Blue Ridge Parkway small.jpg)
 
@@
 
-* `data` Original raw files including the primary result of the search in the Web of Science, and search notes.
+* `data` Primary data files including the SylvanSeeds database in csv format and Boolean search string used in the Web of Science.
 * `doc` Files to create the [manuscript](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md) using `Rmarkdown`.
-* `results` Output of the `R` scripts, including the clean database and files needed to create the manuscript.
-* `src` Scripts in `R` language used to clean the raw data, perform the analyses of the manuscript, and build the `SylvanSeeds` app.
+* `results` Output of the `R` scripts, including files needed to create the manuscript and run the app.
+* `src` Scripts in `R` language used to clean data, perform analyses, and build the `SylvanSeeds` app data.
 

### 2020-11-12 doc/manuscript.Rmd
revised folder structure 🍂

@@
 
-The database is provided as a *csv* file, comma separated [(**Appendix S5**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv).
+The database is provided as a *csv* file, comma separated [(**Appendix S5**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/data/TBMF_Database.csv).
 The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment).
@@
 [**Appendices S1-S4**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf) PRISMA 2009 flow chart describing the process of reference screening and inclusion; bibliography in BibTeX format listing the not-found full texts, the non-relevant references and the relevant references included in the *SylvanSeeds* database.
-[**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv) *SylvanSeeds* database in a single *.csv* file.
+[**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/data/TBMF_Database.csv) *SylvanSeeds* database in a single *.csv* file.
 
@@
 All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database.
-The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates.
+The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/data/TBMF_Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates.
 It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/.

### 2020-11-12 src/cleaning.r

@@ -4,17 +4,17 @@ library(tidyverse); library(here); library(sp); library(openxlsx)
 
 ## TPL Names from common source
 
-read.csv("../#tpl/results/TPLNames.csv") -> Names # TPL taxonomy files are in my home drive
-read.csv("../#tpl/results/Families.csv") -> SeedFamilies # TPL taxonomy files are in my home drive
+read.csv("../#data/tpl/results/TPLNames.csv") -> Names # TPL taxonomy files are in my home drive
+read.csv("../#data/tpl/results/Families.csv") -> SeedFamilies # TPL taxonomy files are in my home drive
 
 ## Clean species file
 
 rbind(
-  read.csv("../#plots/data/sPlot12/species_Edu.csv") %>% # sPlot vegetation files are in my home drive
+  read.csv("../#data/plots/data/sPlot12/species_Edu.csv") %>% # sPlot vegetation files are in my home drive
     select(PlotObservationID, species, Relative.cover) %>%
     rename(Cover = Relative.cover, PlotID = PlotObservationID, Taxon = species) %>%
     mutate(PlotID = paste("Rest", PlotID, sep = "_")),
-  read.csv("../#plots/data/sPlot12/forest2_1500.csv", sep = "\t") %>% # sPlot vegetation files are in my home drive
+  read.csv("../#data/plots/data/sPlot12/forest2_1500.csv", sep = "\t") %>% # sPlot vegetation files are in my home drive
     select(Relevé.number, Species.name, Cover..) %>%
     rename(Cover = Cover.., PlotID = Relevé.number, Taxon = Species.name) %>%
     mutate(PlotID = paste("Japan", PlotID, sep = "_"))) %>%
@@ -25,7 +25,7 @@ rbind(
 ## Clean plot header file
 
 rbind(
-  read.csv("../#plots/data/sPlot12/TDFNH3_Edu.csv") %>% # sPlot vegetation files are in my home drive
+  read.csv("../#data/plots/data/sPlot12/TDFNH3_Edu.csv") %>% # sPlot vegetation files are in my home drive
     filter(Herbs.identified..y.n. != "N" | 
              ! Plants.recorded %in% c("All trees & dominant shrubs", 
                                       "All woody species", 
@@ -42,9 +42,9 @@ rbind(
            Latitude = POINT_Y) %>%
     mutate(PlotID = paste("Rest", PlotID, sep = "_")),
   
[…]

### 2021-05-16 README.Rmd
journal issue 🌅

@@
 
-> Fernández-Pascual E (2021) [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science.*
+> Fernández-Pascual E (2021) [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science* 32, e12960.
